# Sympathy and Urgency {#sympathy-urgency}

Summary statistics of sympathy and urgency

```{r}
summary(trials$sympathy, digits = 2)
summary(trials$urgent, digits = 2)
```

Distribution of the followup questions

```{r, fig.align='center'}
ggplot(trials) + itheme +
  geom_bar(aes(urgent, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Urgent", y = "Proportion", title = "Urgent Distribution", subtitle = "\"Her situation is urgent.\"")
```

```{r, fig.align='center'}
ggplot(trials) + itheme +
  geom_bar(aes(sympathy, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Sympathy", y = "Proportion", title = "Sympathy Distribution", subtitle = "\"Her situation is one I sympathize with.\"")
```

```{r, fig.align='center'}
ggplot(trials) + itheme +
  geom_bar(aes(as.factor(urgent), fill = cond_metaphor), width = 0.9, position = position_dodge2(preserve = "single")) +
  labs(x = "Urgent", y = "Count", title = "Urgent Distribution", subtitle = "\"Her situation is urgent.\"") +
  scale_fill_brewer(palette = "Pastel1")
```

```{r, fig.align='center'}
ggplot(trials) + itheme +
  geom_bar(aes(as.factor(sympathy), fill = cond_metaphor), width = 0.9, position = position_dodge2(preserve = "single")) +
  labs(x = "Sympathy", y = "Count", title = "Sympathy Distribution", subtitle = "\"Her situation is sympathy\"") +
  scale_fill_brewer(palette = "Pastel1")
```

## Sympathy

Does the metaphorical condition have a relationship to participant's rating of perceived sympathy?

H: Higher sympathy leads to higher donations

```{r}
model_sympathy_base = lm(update(base.formula, donation ~ .), data = trials)
model_sympathy_full = lm(update(base.formula, donation ~ . + sympathy), data = trials)

compare_lm(model_sympathy_base, model_sympathy_full)
```

## Urgency

```{r}
# b = trials %>%
#   ggplot(aes(factor(urgent+1), donation)) + ptheme +
#   # geom_boxplot()
#   stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
#   stat_summary(geom = "point", fun.data = mean_se, shape = 5) +
#   geom_jitter(alpha = 0.02, width = 0.25, shape = 16) +
#   scale_x_discrete(labels = c("1" = "1\nNot urgent", "7" = "7")) +
#   scale_y_continuous(labels = scales::dollar) +
#   labs(y = "Donation", x = "Urgency", title = "Urgency on Donation") +
#   coord_cartesian(ylim = c(5, 36))
# 
# b
```

Does the metaphorical condition have a relationship to participant's rating of perceived urgency?

H: High urgency leads to higher donations

```{r}
model_urgent_base = lm(update(base.formula, donation ~ .), data = trials)
model_urgent_full = lm(update(base.formula, donation ~ . + urgent), data = trials)

compare_lm(model_urgent_base, model_urgent_full)
```

## Metaphor on Sympathy

```{r}
# a = trials %>%
#   # mutate(cond_metaphor = factor(cond_metaphor, levels = c("literal", "journey", "battle"))) %>%
#   ggplot(aes(cond_metaphor, urgent+1)) + ptheme +
#   stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.1, position = position_dodge(width = 0.3)) +
#   stat_summary(geom = "point", fun.data = mean_se, shape = 5, position = position_dodge(width = 0.3)) +
#   scale_x_discrete(labels = c("literal" = "Literal", "battle" = "Battle", "journey" = "Journey")) +
#   labs(title = "Metaphor Condition on Urgency", x = "Metaphor", y = "Urgency (1 - 7)") +
#   # scale_color_brewer(palette = "Set1", name = "Gender") +
#   coord_cartesian(ylim = c(5.35, 6.2)) +
#   geom_signif(comparisons = list(c("journey", "battle"), c("literal", "battle")),
#               y_position = c(5.8, 5.95),
#               tip_length = 0.005,
#               textsize = 2.75,
#               annotations = c("list({\U03C7^2}(1) == 10.4, ~~ p < 0.01)", 
#                               "list({\U03C7^2}(1) == 7.8, ~~ p < 0.01)"),
#               parse = T)
# 
# g = grid.arrange(a, b, nrow = 1)
# ggsave("urgency.png", g, width = pwidth, height = pheight, bg = "transparent")
```


The metaphor condition predicts how much sympathy participants feel

```{r}
model_sympathy_base = lm(update(base.formula, sympathy ~ .), data = trials)
model_sympathy_full = lm(update(base.formula, sympathy ~ . + cond_metaphor), data = trials)

compare_lm(model_sympathy_base, model_sympathy_full)
```

## Metaphor on Urgency

The metaphor condition predicts how much urgency participants feel

```{r}
model_urgent_base = lm(update(base.formula, urgent ~ .), data = filter(trials, cond_metaphor != "literal"))
model_urgent_full = lm(update(base.formula, urgent ~ . + cond_metaphor), data = filter(trials, cond_metaphor != "literal"))

compare_lm(model_urgent_base, model_urgent_full)
```

## Cancer Experience on Sympathy

```{r}
model_selfcancer_sympathy_base = lm(update(base.formula, sympathy ~ . - self_cancer), data = trials)
model_selfcancer_sympathy_full = lm(update(base.formula, sympathy ~ .), data = trials)

compare_lm(model_selfcancer_sympathy_base, model_selfcancer_sympathy_full)
```

```{r}
model_ffcancer_sympathy_base = lm(update(base.formula, sympathy ~ . - ff_cancer), data = trials)
model_ffcancer_sympathy_full = lm(update(base.formula, sympathy ~ .), data = trials)

compare_lm(model_ffcancer_sympathy_base, model_ffcancer_sympathy_full)
```

## Cancer Experience on Urgency

```{r}
model_selfcancer_urgent_base = lm(update(base.formula, urgent ~ . - self_cancer), data = trials)
model_selfcancer_urgent_full = lm(update(base.formula, urgent ~ .), data = trials)

compare_lm(model_selfcancer_urgent_base, model_selfcancer_urgent_full)
```

```{r}
model_ffcancer_urgent_base = lm(update(base.formula, urgent ~ . - ff_cancer), data = trials)
model_ffcancer_urgent_full = lm(update(base.formula, urgent ~ .), data = trials)

compare_lm(model_ffcancer_urgent_base, model_ffcancer_urgent_full)
```

## Summary
