# Descriptions {#descriptions}


### Quality

H: Higher quality descriptions lead to more pronounced effects of metaphor

```{r}
on = c("tf3xonytl4jagsno9cql",
"smh4v9rqeytrb2yegyqw",
"b0cfxvjb6q2vya1cesbo",
"3b9w0bh94du4phw3wsos",
"reqfg8cx246zoszmrnff",
"3dkdcw9ekafjqz1v2w87",
"hct0sxcek1473jxxe8fl",
"xznwx3jeunh9jk5lh787",
"f2rmnlfbsanlttcfne6y",
"fpyospteggoemb59nuxw",
"m77sun1swt96wjlejhj6",
"87swbk6cknu3hdbmapv5",
"8wvbwfbnuwpumphgu940",
"xz0dwsq3erfumzdk6g3u",
"6yv9fs9rw94r7q9eph9c",
"lzpwuq5kjk1clpq2lt16",
"2jzymuz60avswfz729e6",
"vqbjja5qhfyvdcvakwur",
"7srebzx2pfdv2yx03v05",
"tdv6duh9sarj5s60pwm3",
"z5brs0mevdumpjuevm8v",
"kt20270j5t571c8z3xn9",
"cccex8n929kjh1y8mzre",
"tn0jgbbqmhghfw196c61",
"xp86x9vm339usdvxlfza",
"t3lu8b4ftr1by3lpap4e",
"xyofqyp1nh9q97v9wfyr",
"lkbdt5nzgzmkhurkkwye",
"zphy1s3uahrw79lo6mgb",
"0w96jzbx6rdxxs1ennv1",
"4rd5bhz5mbns2md570oc",
"ahc5yd008ex82nru2km3",
"yzd7ffgsxonycgctlwga",
"yo8hsz0wgqzm509mght8",
"1dj947x3sc3yy2wuvvya",
"mxz5ekm89vlybuhn45mf",
"pbja5q8hatb1x8pznvb4",
"tc64drmbb8x3uyr99lab",
"ja3fc6jnmpma4hm93w63",
"g6jnvll7m4fxlu5nb2my",
"pwge07onacepsxu8ba4j",
"kghh5kbbucbp2mndl166",
"cd7f7jhhw8ktzobf5fg2",
"buhomawfdyuurlb0nnre",
"24g8fky5nr8myjgjv1au",
"5ca7r126ycutz4435shn",
"dy96zubatwjfjnoafvq7",
"o963w232hcuton7o0wwe",
"yrymka12ud48yor18fgs",
"165hlrnwg8zjg0kkd326",
"xzutvogrmy61h1uhmsms",
"vzrg2pv9yx73wdy1vrjf",
"wg0gstttpx8chpre3u4y",
"su4l0tfwd1bmt97epd8v",
"g45swcjf8fdr5g3o486h",
"50s8fq827n3j3xb2pge1",
"v8aauzyac07yh0dw57j5",
"99bujlc9qce15w9kkq3w",
"x3elx8ryobdby1qskvle",
"9qyfkvaqwdenrguloyck",
"fyrxw8fvway3odnpx7k7",
"1ta7ybxtkrz9ooc76cvc",
"0ajaoxsy3347gmp5cazv",
"34tqgyvfj9n2cb0y0jok",
"sum9001yhghvel368vlp",
"c4hw391phy51jro89k0j",
"6rfmwmzr79ozthsvraug",
"484fpe4p96clmbe7n0t8",
"qkfy72l6ejvbop9ancku",
"jzlusqash832fk2ex4k1",
"zb21gmjo80u9ek8rd8nw",
"x2qk2ah2h3e2r7qylde5",
"jqcf9p69pkyu7gskhtyr",
"bvrgr53v0g5nlqz0xb6g",
"sp9byj7fyme5tt5om2ug",
"kg9hm5p8q9e27x6o15y4",
"71h2qmqd9rygbn0t61lz",
"fdf356gfqc40gbbuavtc")

off = c(
  "hhw1u9my0wb4mmloq5y1",
  "qfuprcslsqhvsj8m0204",
  "om5tgdnye66bl2op1gn9",
  "laol6h7mwr9vo7ck33pa",
  "x7shu9mtsmpkepgvw8x0",
  "wffsbmhstf2k0ttl0g62",
  "yy5wq00249pxqchykw10",
  "6h4czt8gx5la9zm1fkdk",
  "0my60drm8ju1mw1c6aza",
  "3o12tk6lf73ykhpwop0o",
  "7hmwgza7hkmrn7zhq2n6",
  "aqv3l25op1er93152tl1",
  "wl17338rdug8ga22xeo6",
  "naqlakmus7gzy4y962ge",
  "fzbdpsr2n7o8q1pgk8h2",
  "hzp8n2szsjvw3j3pz6dd",
  "va5md1g5j1cmw5pb8v78",
  "6dt1dlktrcgsb68yeyko"
)

trials[trials$ppt %in% on, "on_topic"] = 1
trials[trials$ppt %in% off, "on_topic"] = 0
```

```{r}
m1 = lm(update(base.formula, donation ~ .), data = filter(trials, on_topic == 1))
m2 = lm(update(base.formula, donation ~ . + on_topic), data = filter(trials, on_topic == 1))

summary(m2)
```


### Metaphor

Define some keywords under two main families and one exploratory family of metaphor (only lemmas).

```{r}
BATTLE_PHRASES <- c('\\bfight', '\\bfought\\b', '\\bbattling\\b', '\\bbattle', '\\bwar\\b', '\\bbeat', '\\benemy\\b', '\\bdefeat\\b', 
                    '\\bwin\\b', '\\bcombat\\b', '\\bconquer\\b', '\\bovercome\\b', '\\bkill\\b')

JOURNEY_PHRASES <- c('\\bpath\\b', '\\bjourney\\b', '\\broad\\b', '\\brollercoaster\\b', '\\bon track\\b')

# FORCE_PHRASES <- c('forced', 'force', 'lava', 'flood', 'volcano', 'wave', 'drown', 'storm', 'disaster', 'river')
```

Run a search over descriptions for the keywords and count their occurances. 

```{r}
search_description_for_battle <- function(row) {
  return(sum(sapply(BATTLE_PHRASES, function (k) grepl(k, tolower(row)))))
}

search_description_for_journey <- function(row) {
  return(sum(sapply(JOURNEY_PHRASES, function (k) grepl(k, tolower(row)))))
}

# search_description_for_force <- function(row) {
#   return(sum(sapply(FORCE_PHRASES, function (k) grepl(k, tolower(row), fixed = T))))
# }
```

```{r}
labeled <- read_csv("../experimental/data/free_responses_pre15.csv")

labeled$auto_battle = unname(sapply(labeled$description, search_description_for_battle))
labeled$auto_journey = unname(sapply(labeled$description, search_description_for_journey))

labeled <- labeled[, c("ppt", "journey", "battle", "auto_battle", "auto_journey")]
colnames(labeled) <- c("ppt", "desc_journey_present", "desc_battle_present", "auto_battle", "auto_journey")
labeled$desc_journey_present <- labeled$desc_journey_present > 0
labeled$desc_battle_present <- labeled$desc_battle_present > 0

trials_with_desc_count <- left_join(trials, labeled)
```

```{r}
trials_with_desc_count_fil <- trials_with_desc_count[!is.na(trials_with_desc_count$desc_journey_present), ]

table(trials_with_desc_count_fil$desc_journey_present, trials_with_desc_count_fil$auto_journey)
table(trials_with_desc_count_fil$desc_battle_present, trials_with_desc_count_fil$auto_battle)
```

```{r}
trials_with_desc_count_fil %>% 
  filter(desc_battle_present != auto_battle) %>%
  dplyr::select(description, desc_journey_present, auto_journey, desc_battle_present, auto_battle) %>%
  as.matrix()
```

```{r}
trials$battle_presv = unname(sapply(trials$description, search_description_for_battle))
trials$journey_presv = unname(sapply(trials$description, search_description_for_journey))

trials$description_metaphor =
  case_when(trials$battle_presv > 0 & trials$journey_presv == 0 ~ "battle",
            trials$journey_presv > 0  & trials$battle_presv == 0 ~ "journey",
            trials$battle_presv > 0 & trials$journey_presv > 0 ~ "mixed",
            trials$battle_presv == 0  & trials$journey_presv == 0 ~ "none")

trials$description_metaphor = factor(trials$description_metaphor, levels = c("none", "mixed", "journey", "battle"))
```

```{r}
trials$word_count = sapply(trials$description, function(t) str_count(t, " ")+1)

sum(trials$battle_presv) / sum(trials$word_count) * 1000
sum(trials$journey_presv) / sum(trials$word_count) * 1000
```

Approxiamtely 9.5 battle metaphors per 1,000 words and 2.9 journey metaphors per 1,000 words overall.

```{r, fig.align='center'}
trials %>%
  ggplot(aes(cond_metaphor, 1000 * battle_words / word_count)) + itheme +
  geom_errorbars +
  coord_cartesian(ylim = c(0, 20)) +
  labs(title = "Battle Metaphor Frequency by Metaphor Condition")
```

```{r, fig.align='center'}
trials %>%
  ggplot(aes(cond_metaphor, 1000 * journey_words / word_count)) + itheme +
  geom_errorbars +
  coord_cartesian(ylim = c(0, 10)) +
  labs(title = "Journey Metaphor Frequency by Metaphor Condition")
```

```{r}
round(100*mean(trials$description_metaphor == "battle"), 2)
round(100*mean(trials$description_metaphor == "journey"), 2)
round(100*mean(trials$description_metaphor == "mixed"), 2)
round(100*mean(trials$description_metaphor == "none"), 2)
```

About 22% of participants preserved a metaphor: 16% preserved a battle metaphor, 5% preserved a journey metaphor, and 1.3% preserved both metaphors.

#### Effect of Metaphor Condition on preserved Metaphor in Description

```{r}
g = trials %>%
  filter(description_metaphor %in% c("battle", "journey", "mixed")) %>%
  # group_by( cond_metaphor, description_metaphor) %>%
  # summarize(prop = n() / nrow(trials)) %>%
  ggplot(aes(cond_metaphor, group = description_metaphor, fill = description_metaphor)) + ptheme +
  # geom_point() +
  # geom_line() +
  geom_bar(position = "dodge") +
  # scale_y_continuous(labels = scales::percent) +
  # scale_x_discrete(labels = c("literal" = "Literal", "battle" = "Battle", "journey" = "Journey")) +
  labs(title = "Number of Participants with Preserved Metaphor by Condition",
       x = "Metaphor Condition",
       y = "# of Responses",
       fill = "Metaphor Preserved")
  # scale_color_brewer(palette = "Set1", name = "Metaphors\nPreserved", labels = c("mixed" = "Mixed", "journey" = "Journey", "battle" = "Battle")) +
  # coord_cartesian(ylim = c(0.0, 0.1))

g
# ggsave("preserved_metaphor.png", g, width = pwidth, height = pheight, bg = "transparent")
```

Does the preservation of the same metaphor which the ppt was exposed to mediate donation amount?

Does donation behavior change when the ppt preserves the metaphor

Preservation is comprehension, engagement, care, focus, attention

Ppts who preserve the metaphor might 

Does preservation predict donation amount, or does donation amount predict the preservation?

Why is it interesting if people are preserving metaphors?
  Shows something about the impact that the appeal has on the ppt's framing of the situation?
  Ppts who preserve the exposed metaphor seem to have their framing influenced?
  If their framing is influenced, does that change how much they donated?
  so what? to affect one's donation, it's important that their framing is changed
  
  literal condition is a baseline for how much we might expect the metaphor to be preserved
  
  donations for individuals that preserve a battle metaphor 
  
  
```{r}
trials$preservation = as.integer(trials$journey_presv > 0)

journey_mask <- trials$cond_metaphor != "battle"


m1 <- glm(update(base.formula, preservation ~ .), 
          data = trials[journey_mask, ],
          family = "binomial")
m2 <- glm(update(base.formula, preservation ~ . + cond_metaphor), 
          data = trials[journey_mask, ],
          family = "binomial")


m3 <- lm(update(base.formula, donation ~ . + preservation + cond_metaphor),
         data = trials[journey_mask, ])

# compare_lm(m1, m2)

med <- mediate(m2, m3,
               treat = "cond_metaphor", mediator = "preservation", 
               boot = T, boot.ci.type = "perc", sims = 1000)

summary(med)
```




We analyzed the free-response answers the participants completed in response to being asked to explain the patient's situation to a friend. We were interested in whether the metaphor in the passage predicts the presence of metaphors in the description. We will model this with a logistic regression, accounting for the covariates included in the primary hypothesis model.

```{r}
trials$preserved_metaphor = trials$description_metaphor != "none"

model_metaphor_preserve_base = glm(update(base.formula, preserved_metaphor ~ .), 
                                   data = trials, 
                                   family = "binomial")
model_metaphor_preserve_full = glm(update(base.formula, preserved_metaphor ~ . + cond_metaphor), 
                                   data = trials, 
                                   family = "binomial")

compare_lm(model_metaphor_preserve_base, model_metaphor_preserve_full)
```

In both metaphor conditions, we see a significant increase in the likelihood that the participant will go on to use some sort of metaphor.

```{r}
model_metaphor_preserve_base = glm(update(base.formula, I(description_metaphor == "journey") ~ .), 
                                   data = trials %>%
                                     filter(cond_metaphor %in% c("journey", "battle"), 
                                            description_metaphor %in% c("journey", "battle")), 
                                   family = "binomial")
model_metaphor_preserve_full = glm(update(base.formula, I(description_metaphor == "journey") ~ . + cond_metaphor), 
                                   data = trials %>% 
                                     filter(cond_metaphor %in% c("journey", "battle"),
                                            description_metaphor %in% c("journey", "battle")), 
                                   family = "binomial")

compare_lm(model_metaphor_preserve_base, model_metaphor_preserve_full)
```

In both metaphor conditions, we see a significant increase in the likelihood that the participant will go on to use a journey metaphor.

```{r, fig.align='center'}
trials %>%
  filter(cond_metaphor %in% c("journey", "battle"),
         description_metaphor %in% c("journey", "battle")) %>%
  ggplot() +
  geom_bar(aes(cond_metaphor, fill = description_metaphor), position = "dodge")
```


```{r}
model_metaphor_preserve_base = glm(update(base.formula, I(description_metaphor == "battle") ~ .), 
                                   data = trials %>%
                                     filter(cond_metaphor %in% c("journey", "battle"), 
                                            description_metaphor %in% c("journey", "battle")), 
                                   family = "binomial")
model_metaphor_preserve_full = glm(update(base.formula, I(description_metaphor == "battle") ~ . + cond_metaphor), 
                                   data = trials %>% 
                                     filter(cond_metaphor %in% c("journey", "battle"),
                                            description_metaphor %in% c("journey", "battle")), 
                                   family = "binomial")

compare_lm(model_metaphor_preserve_base, model_metaphor_preserve_full)
```

In the battle metaphor condition, we see a significant increase in the likelihood that the participant will go on to use a battle metaphor. This increase does not exist for participants who were exposed to journey metaphors.

#### Effect of Preserved Metaphor on Donation Behavior

Additionally, we are interested in knowing whether preserved metaphor usage in responses predicts a main effect of donation amount. We will model this with an ordinary linear regression model, accounting for the same covariates as the other models.

```{r}
model_preserved_base = lm(update(base.formula, donation ~ .), data = trials)
model_preserved_full = lm(update(base.formula, donation ~ . + preserved_metaphor), data = trials)

compare_lm(model_preserved_base, model_preserved_full)
```

#### Interaction of Preserved Metaphor on Donation Behavior

```{r}
print_crosstabs(ftable(trials$cond_metaphor, trials$description_metaphor))
```

```{r, fig.align='center'}
trials %>%
  filter(description_metaphor != "mixed") %>%
  ggplot(aes(cond_metaphor, donation, color = description_metaphor)) + itheme +
  geom_errorbars +
  coord_cartesian(ylim = c(20, 32))
```


NH: Donation amounts do not differ between participants who preserve the metaphor they were exposed to and those who did not preserve any metaphor.

```{r}
model_preserved_base = lm(update(base.formula, donation ~ . + cond_metaphor), 
                          data = trials) #filter(trials, description_metaphor != "none"))
model_preserved_mid = lm(update(base.formula, donation ~ . + cond_metaphor + description_metaphor), 
                         data =  trials) #filter(trials, description_metaphor != "none"))
model_preserved_full = lm(update(base.formula, donation ~ . + cond_metaphor * description_metaphor), 
                          data =  trials) #filter(trials, description_metaphor != "none"))

compare_lm(model_preserved_base, model_preserved_mid)
compare_lm(model_preserved_mid, model_preserved_full)
```

```{r}
model_urgent_base = lm(update(base.formula, urgent ~ .), 
                       data = filter(trials, description_metaphor != "none"))
model_urgent_full = lm(update(base.formula, urgent ~ . + I(description_metaphor == "battle")), 
                       data = filter(trials, description_metaphor != "none"))

compare_lm(model_urgent_base, model_urgent_full)
```

## Summary