# Mediation {#mediation}

https://crumplab.github.io/psyc7709/book/docs/bootstrapped-mediation-tutorial.html

https://www.annualreviews.org/doi/pdf/10.1146/annurev.psych.58.110405.085542


We will use the responses to the questions about perceived urgency and sympathy toward the patient as variables in a mediation analysis to explore their role in mediating metaphor's effect on donation amounts.

Steps to establishing mediation via tests of causal steps, from Baron & Kenny (1986) [BK86]:

  1. "a significant relation of the independent variable to the dependent variable is required"
  2. "a significant relation of the independent variable to the hypothesized mediating variable is required"
  3. "the mediating variable must be significantly related to the dependent variable when both the independent variable and mediating variable are predictors of the dependent variable"
  
Alternatively, we may use resampling techniques (e.g. bootstrap) to create confidence intervals on the indirect effect and therefore construct a NHT.

The two mediation techniques aren't neccessarily mutually exclusive, however using BCa bootstrapped CIs tends to lead to much higher power (Fritz & MacKinnon, 2007) and doesn't rely on the same assumptions (although similarities exists).

```{r}
library(crayon)
library(glue)
library(mediation)
```

Set up a few helper functions to identify mediation models worth running.

```{r}
check_BK86_assumption_1 = function (total_effect_pvalue, type_i_error) {
  if (total_effect_pvalue < type_i_error) print(glue_col("{green The total effect of X on Y is significant.}"))
  else print(glue_col("{red The total effect of X on Y is not significant.}"))
}

check_BK86_assumption_2 = function (alpha_pvalue, type_i_error) {
  if (alpha_pvalue < type_i_error) print(glue_col("{green The effect of X on M is significant.}"))
  else print(glue_col("{red The effect of X on M is not significant.}"))
}

check_BK86_assumption_3 = function (beta_pvalue, type_i_error) {
  if (beta_pvalue < type_i_error) print(glue_col("{green The effect of M on Y controlled for X is significant.}"))
  else print(glue_col("{red The effect of M on Y controlled for X is not significant.}"))
}

check_BK86_assumption_4 = function (direct_effect, total_effect, direct_effect_pvalue, type_i_error) {
  partial <- abs(direct_effect) < abs(total_effect)
  
  if (direct_effect_pvalue >= type_i_error) {
    print(glue_col("{green The direct effect of X on Y adjusted for M is non-significant.}"))
  } else if (partial) {
    print(glue_col("{yellow The direct effect of X on Y adjusted for M is less than the total effect of X on Y.}"))
  } else {
    print(glue_col("{red The direct effect is significant or greater than the total effect.}"))
  }
}

check_mediation_assumptions = function (dv, md, iv, iv_key, data) {
  
  formula_covars <- as.character(base.formula)[2]
  type_i_error <- 0.1
  
  model_x_m <-  summary(lm(reformulate(c(formula_covars, iv), md), data = data))
  model_mx_y <- summary(lm(reformulate(c(formula_covars, md, iv), dv), data = data))
  model_x_y <-  summary(lm(reformulate(c(formula_covars, iv), dv), data = data))
  
  total_effect <-   model_x_y$coefficients[iv_key, ]
  direct_effect <-  model_mx_y$coefficients[iv_key, ]
  beta <-           model_mx_y$coefficients[md, ]
  alpha <-          model_x_m$coefficients[iv_key, ]
  
  print(glue("total effect = {round(total_effect[1] / total_effect[2], 2)}, direct effect = {round(direct_effect[1] / direct_effect[2], 2)}, beta = {round(beta[1] / beta[2], 2)}, alpha = {round(alpha[1] / alpha[2], 2)}"))
  print(glue("indirect effect = {round((alpha[1] / alpha[2]) * (beta[1] / beta[2]),3)}"))
  
  check_BK86_assumption_1(model_x_y$coefficients[iv_key, 4], type_i_error)
  
  check_BK86_assumption_2(model_x_m$coefficients[iv_key, 4], type_i_error)
  
  check_BK86_assumption_3(model_mx_y$coefficients[md, 4], type_i_error)
  
  check_BK86_assumption_4(direct_effect[1], total_effect[1], model_mx_y$coefficients[iv_key, 4], type_i_error)
}
```

## Any Metaphor to Literal condition

The presence of Any Metaphor did not significantly predict donation, so mediation analysis is irrelevant here for sympathy and urgency.

## Battle to Literal condition

### Sympathy

Does Sympathy mediate the relation between metaphor condition (between battle and literal conditions) and donation amounts?

```{r}
mask <- trials$cond_metaphor != "journey"

check_mediation_assumptions("donation", "sympathy", "cond_metaphor", "cond_metaphorbattle", trials[mask, ])
```

### Urgency

Does Urgency mediate the relation between metaphor condition (between battle and literal conditions) and donation amounts?

```{r}
mask <- trials$cond_metaphor != "journey"

check_mediation_assumptions("donation", "urgent", "cond_metaphor", "cond_metaphorbattle", trials[mask, ])
```

## Journey to Literal condition

### Sympathy

Does Sympathy mediate the relation between metaphor condition (between journey and literal conditions) and donation amounts?

```{r}
mask <- trials$cond_metaphor != "battle"

check_mediation_assumptions("donation", "sympathy", "cond_metaphor", "cond_metaphorjourney", trials[mask, ])
```

### Urgency

Does Urgency mediate the relation between metaphor condition (between journey and literal conditions) and donation amounts?

```{r}
mask <- trials$cond_metaphor != "battle"

check_mediation_assumptions("donation", "urgent", "cond_metaphor", "cond_metaphorjourney", trials[mask, ])
```

## Battle to Journey condition

These tests of mediation are the only ones which satisfy the first causal step for determining mediation (an alternative to resampling). This is a critical relationship, and because it holds here, we will also test the significance of the indirect effect using the bootstrap.

### Sympathy

Does Sympathy mediate the relation between metaphor condition (between battle and journey conditions) and donation amounts?

```{r}
mask <- trials$cond_anymet

check_mediation_assumptions("donation", "sympathy", "cond_metaphor", "cond_metaphorjourney", trials[mask, ])
```

We remove the OptOut level of the gender factor due to numerical computation issues.

```{r}
ggplot() +
  geom_jitter(aes(sympathy, donation, color = cond_metaphor), alpha = 0.5, data = temp_data) +
  geom_vline(xintercept = coef(model_x_m)["(Intercept)"]) +
  geom_vline(xintercept = coef(model_x_m)["(Intercept)"] + coef(model_x_m)["cond_metaphorjourney"]) +
  geom_abline(intercept = coef(model_mx_y)["(Intercept)"],
              slope = coef(model_mx_y)["sympathy"]) +
  geom_abline(intercept = sum(coef(model_mx_y)[c("(Intercept)", "cond_metaphorjourney")]),
              slope = coef(model_mx_y)["sympathy"])
```


```{r battle_journey_sympathy_mediation}
temp_data <- trials[mask, ] %>% 
  filter(gender != "OO") %>%
  mutate(cond_metaphor = factor(cond_metaphor))

model_x_m <- lm(update(base.formula, sympathy ~ . + cond_metaphor), 
                data = temp_data)
model_mx_y <- lm(update(base.formula, donation ~ . + sympathy + cond_metaphor), 
                 data = temp_data)
  
med.anlys <- mediate(model.m = model_x_m,
                    model.y = model_mx_y, 
                    treat = "cond_metaphor",
                    mediator = "sympathy",
                    boot = T, 
                    boot.ci.type = "bca",
                    sims = 2000)

summary(med.anlys)
```

Based upon Baron & Kenny's (1986) causal-steps, sympathy cannot mediate the relation between metaphor condition and donation amount. Moreover, based upon resampling, the same conclusion is also drawn.

### Urgency

Does Urgency mediate the relation between metaphor condition (between battle and journey conditions) and donation amounts?

```{r}
mask <- trials$cond_anymet

check_mediation_assumptions("donation", "urgent", "cond_metaphor", "cond_metaphorjourney", trials[mask, ] %>% sample_n(1000))
```

For an alpha of magnitude -0.15 and a beta of magnitude 3.23, we should expect, according to Fritz and MacKinnon (2007), a required sample size of 385 participants for 80% power (and 5% type I error). We'll keep this in mind for testing the hold-out set.

```{r battle_journey_urgency_mediation}
temp_data <- trials[mask, ] %>%
  filter(gender != "OO")
  #        gender != "OO",
  #        education != "<HS",
  #        education != "OO",
  #        self_cancer != "OO",
  #        ff_cancer != "OO",
  #        socioeconomic != "OO") %>%
  # sample_n(1000)

model_x_m <- lm(update(base.formula, urgent ~ . + cond_metaphor), 
                data = temp_data)
model_mx_y <- lm(update(base.formula, donation ~ . + urgent + cond_metaphor), 
                 data = temp_data)

# summary(model_x_m)$coefficients[, c(1,2)]

med.anlys <- mediate(model.m = model_x_m,
                    model.y = model_mx_y,
                    treat = "cond_metaphor",
                    mediator = "urgent", 
                    boot = T, 
                    boot.ci.type = "bca",
                    sims = 2000)

summary(med.anlys)
```

```{r}
temp_data <- trials[mask, ] %>%
  filter(gender != "OO") %>%
  mutate(cond_metaphor = factor(cond_metaphor))

model_x_m_r <- lm(update(base.formula, donation ~ . + cond_metaphor), 
                data = temp_data)
model_mx_y_r <- lm(update(base.formula, urgent ~ . + donation + cond_metaphor), 
                 data = temp_data)

med.anlys <- mediate(model.m = model_x_m_r,
                    model.y = model_mx_y_r,
                    treat = "cond_metaphor",
                    mediator = "donation", 
                    boot = T,
                    boot.ci.type = "bca",
                    sims = 2000)

summary(med.anlys)
```

```{r}
mm <- model.matrix(update(base.formula, donation ~ . + urgent + cond_metaphor), 
                 data = temp_data)

3.75313643 * sd(mm[, "urgent"]) / sd(temp_data$donation) # b
-2.3086208 * sd(mm[, "cond_metaphorjourney"]) / sd(temp_data$donation) # c'

-0.1475918 * sd(mm[, "cond_metaphorjourney"]) / sd(temp_data$donation) # a
```

```{r}
ggplot() +
  geom_jitter(aes(urgent, donation, color = cond_metaphor), alpha = 0.5, data = temp_data) +
  geom_vline(xintercept = coef(model_x_m)["(Intercept)"]) +
  geom_vline(xintercept = coef(model_x_m)["(Intercept)"] + coef(model_x_m)["cond_metaphorjourney"]) +
  geom_abline(intercept = coef(model_mx_y)["(Intercept)"],
              slope = coef(model_mx_y)["urgent"]) +
  geom_abline(intercept = sum(coef(model_mx_y)[c("(Intercept)", "cond_metaphorjourney")]),
              slope = coef(model_mx_y)["urgent"])
```

```{r}
library(lavaan)
```

```{r}
base.formula
```


```{r}
full_med <- '
urgent ~ cond_metaphor + cond_sex + past_donations.z + age.z
donation ~ urgent + cond_sex + past_donations.z + age.z
'

sem_full <- sem(full_med, data = temp_data %>% 
                  mutate(
                    cond_metaphor = scale(as.integer(cond_metaphor)),
                    cond_sex = scale(as.integer(cond_sex))))

partial_med <- '
urgent ~ cond_metaphor + cond_sex + past_donations.z + age.z
donation ~ cond_metaphor + urgent + cond_sex + past_donations.z + age.z
'

sem_partial <- sem(partial_med, data = temp_data %>% 
                  mutate(
                    cond_metaphor = scale(as.integer(cond_metaphor)),
                    cond_sex = scale(as.integer(cond_sex))))
```

```{r}
summary(sem_partial)
```


Based upon Baron & Kenny's (1986) causal-steps, urgency does fully mediate the relation between metaphor condition and donation amount. Moreover, based upon resampling methods, the same conclusion can be drawn.

```{r}
library(tictoc)
```


```{r}
b <- 1000
N_trials <- 2

mediate_sim <- function(data, indices) {
  d <- data[indices, ]
  model_x_m <- lm(update(base.formula, urgent ~ . + cond_metaphor), 
                data = d)
  model_mx_y <- lm(update(base.formula, donation ~ . + urgent + cond_metaphor), 
                 data = d)
  
  a <- coef(model_mx_y)["urgent"]
  # b <- coef(model_x_m)["cond_metaphorjourney"]
  return(unname(a))
}

generate <- function() {
  bs_out <- boot::boot(temp_data, mediate_sim, R = b, parallel = "multicore")
  bs_ci_out <- boot::boot.ci(bs_out, type = "perc")
  
  return(c(est = bs_out$t0, L = bs_ci_out$percent[4], U = bs_ci_out$percent[5]))
}

tic()
trials <- as.data.frame(t(replicate(N_trials, generate())))
toc()
trials
```

```{r}
mean(trials$U < 0)
```


```{r}
m = mean_se(unname(unlist(est[1,])))
m = quantile(unname(unlist(est[1,])), c(0.025, 0.5, 0.975))
m
g = ggplot() + theme_minimal() +
  theme(axis.title = element_blank()) +
  stat_density(geom = "line", aes(c(-1.5, unname(unlist(est[1,])), 0.5))) +
  geom_vline(xintercept = m[2]) +
  geom_vline(xintercept = m[1], color = "red") +
  geom_vline(xintercept = m[3], color = "red") +
  geom_vline(xintercept = 0, linetype = 2) +
  coord_cartesian(xlim = c(-1.5, 0.5))

```



## Summary

Any Metaphor did not significantly predict donation amounts, so we skipped those two mediation checks all together. 

Next, we looked at whether the relation between the battle condition compared to the literal condition and donation amounts was mediated. The metaphor condition did not predict donation amounts, so we don't run these mediation analyses either.

A similar story holds for the journey condition compared to the literal condition.

Lastly, we checked whether the relation between the battle condition compared to the journey condition and donation amounts was mediated. This is the most promising exploration, since we see a significant difference between the two metaphor conditions. We find that according to BK86, sympathy fails to mediate the relationship since the metaphor condition did not predict sympathy. Likewise, a BCa bootstrap mediation analysis also reports a direct effect and no causal mediation effect. Yet, all four assumptions of BK86 were met when testing urgency's mediation on the conditions. Similarly, a BCa bootstrap mediation analysis reports a highly significant decrease in donation amounts given the journey condition as a direct "causal" mediation of lowered urgency compared to the battle condition.






