--- 
title: "Metaphors on Charitable Donations"
author: "Alex Liebscher"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
description: "Effects of Battle and Journey Metaphors on Charitable Donations for Cancer Patients"
output:
  bookdown::gitbook: default
---

# Prerequisites

Collected here are all exploratory analyses. They are organized by question topic on the left-hand side navigation bar. Summaries of each analysis are contained at the end of each major section/chapter.

## Load Libraries

```{r}
library(tidyverse) # mostly for ggplot2 and dplyr
library(jtools) # for pretty printing model summaries
library(gridExtra) # for combining plots
# library(sysfonts)
# library(showtext) # for custom fonts in presentation graphs
library(ggsignif)
library(glue)
library(crayon)
library(pwr)
```

## Load Data

Created via `exclusion.Rmd`, originally from `clean_data.R`. Here, we trim off some outliers in the `age` and `past_donations` columns (then fill in missing values with the new mean).

```{r}
trials <- read_csv("../../data/data_clean_trial_large_filtered.csv", col_types = cols()) %>%

  # remove outliers in past_donations and age which lie greater than 3 SDs away
  # filter(past_donations < (mean(past_donations, na.rm = T) + 3*sd(past_donations, na.rm = T))) %>%
  # filter(age < (mean(age, na.rm = T) + 3*sd(age, na.rm = T))) %>%
  # filter(age >= 18) %>%
  
  # set the levels of the factors variables and rescale age and past_donations
  mutate(
    cond_sex = factor(cond_sex, levels = c("male", "female")),
    cond_metaphor = factor(cond_metaphor, levels = c("literal", "battle", "journey")),
    cond_anymet = cond_metaphor %in% c("battle", "journey"),

    urgent = as.integer(urgent),
    sympathy = as.integer(sympathy),

    self_cancer = factor(self_cancer, levels = c("N", "Y", "OO")),
    ff_cancer = factor(ff_cancer, levels = c("N", "Y", "OO")),

    gender = factor(gender, levels = c("M", "F", "NB", "OO")),
    education = factor(education, levels = c("<HS", "HS", "A", "B", "M", "P", "D", "OO")),
    socioeconomic = factor(socioeconomic, levels = c("<10k", "10-25k", "25-50k", "50-75k", "75-100k", "100-150k", ">150k", "OO")),
    
    rt_trial_group = factor(rt_trial_group, levels = c("[1.9,23]", "(23,42.7]", "(42.7,69.3]", "(69.3,4.25e+03]")),
    
    congruency = ifelse((gender == "M" & cond_sex == "male") | (gender == "F" & cond_sex == "female"),
                        "congruent",
                        "incongruent")
  )
```

```{r}
# fill in missing values for past_donation and age with their means
trials <- trials %>% 
  replace_na(list(past_donations = mean(trials$past_donations, na.rm = T))) %>%
  replace_na(list(age = mean(trials$age, na.rm = T)))

trials <- trials %>%
  mutate(
    age.z = (age - mean(age)) / (2 * sd(age)),
    past_donations.z = (past_donations - mean(past_donations)) / (2 * sd(past_donations))
  )
```

```{r}
nrow(trials)
```


There are a total of `r nrow(trials)` observations.

Define a common formula used throughout which includes all of the primary covariates, including the patient sex condition.

```{r}
base.formula <- formula( ~ cond_sex + self_cancer + ff_cancer + gender + education + socioeconomic + past_donations.z + age.z)
```

## Build Custom Functions

```{r}
# pretty printing summary contingency tables
print_crosstabs <- function(tab) {
  print(tab)
  cat("\n")
  print(round(prop.table(tab), 3))
}

pvalue_show_summary <- 0.1

compare_lm <- function (base, full, force_summary = F) {
  #' Compare two linear or generalized linear models using a Chisq difference test
  #'
  
  a <- anova(base, full, test = "Chisq")
  print(a)
  print.noquote(paste("Chisq Stat: ", as.numeric(round(2*(logLik(full) - logLik(base)), 3))))
  
  if (a["Pr(>Chi)"][[1]][2] < pvalue_show_summary | force_summary) {
    cls <- attributes(full)$class
    if (cls == c("lm") | cls == c("glm", "lm")) {
      print(summ(full, confint = T, digits = 3))  
    } else {
      print(summary(full))
    }
  }
}
r.sq = function(mod.base, mod.full) {
  #' Calculate the R-squared value given two nested models
  #' 
  #' The variance explained by a full model beyond that which is explained by the reduced model.
  #' Technically, a difference in sum of squared residuals divided by the base model's sum of squared residuals
  #' Adapted from Larsen & Marx (2018) pg. 566
  
  return((sum(resid(mod.base)^2) - sum(resid(mod.full)^2)) / sum(resid(mod.base)^2))
}
f.sq = function(mod.null, mod.base, mod.full) {
  #' Calculate the f-squared effect size from two R-squared values
  #'
  #' Adapted from Cohen (1988) pg. 409
  
  R2.base = r.sq(mod.null, mod.base)
  R2.full = r.sq(mod.null, mod.full)
  
  return((R2.full - R2.base) / (1 - R2.full))
}
```

## Set Custom Plot Themes

```{r}
# font_add("Avenir", "/System/Library/Fonts/Avenir.ttc")
# showtext_auto()

# Rmd interactive theme
itheme <- list(theme_minimal(), scale_color_brewer(palette = "Dark2"))

# Presentation theme
ptheme <- theme_minimal() + theme(
  panel.background = element_rect(fill = "transparent", color = NA),
  plot.background = element_rect(fill = "transparent", color = NA),
  legend.key = element_blank(),
  legend.background = element_rect(fill = "transparent", color = NA),
  text = element_text(family = "Avenir")
)

pwidth = 6.5
pheight = 3
```

Custom ggPlot elements which are used often

```{r}
geom_errorbars <- list(
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.35), width = 0.2), 
  stat_summary(fun.data = mean_se, geom = "point", shape = 5, position = position_dodge(width = 0.35)))
```

