---
title: "Exclusion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Exclusion Criteria

## Load Libraries

```{r}
library(tidyverse)
library(crayon)
library(glue)
```

## Set Global Variables

```{r}
print_exclusion_change <- function(title, start, pre_exclusion, post_exclusion) {
  removed <- pre_exclusion - post_exclusion
  percent_change <- round(-100 * removed / pre_exclusion, 2)
  percent_total_change <- round(100 * (post_exclusion - start) / start, 2)
  print(glue_col("{red {title}: {removed} ({percent_change}%) just removed\tNow: {post_exclusion} ppts ({percent_total_change}% decrease)}"))
}

# bot check correct answers
CHECK1_ANS = 1
CHECK2_ANS = 2

# minimum amount of time required on the stimulus
MINIMUM_TRIAL_RT = 5000 # in Milliseconds
```

## Load Data

Load the data straight from `clean_data.R`. Execution of the steps below *must* occur before the main analysis and exploratory analysis.

```{r}
input.file <- "../data/data_clean_trial_large.csv"
output.file <- "../data/data_clean_trial_large_filtered.csv"

trials <- read_csv(input.file, col_types = cols())

nStart <- nrow(trials)
glue("{format(nStart, big.mark=",")} participants to begin with")
```

## Exclusion Criteria

### Native English check

Exclude ppts who didn't indicate that English was their native language.

```{r}
pre_exclusion = nrow(trials)

trials = trials %>% filter(english == "Y")
print_exclusion_change("Non-Native English", nStart, pre_exclusion, nrow(trials))
```

### Bot check

Exclude ppts who failed to correctly answer the bot check questions

```{r}
pre_exclusion = nrow(trials)

trials = trials %>% filter(check1 == CHECK1_ANS & check2 == CHECK2_ANS)

print_exclusion_change("Failed 1+ bot check questions", nStart, pre_exclusion, nrow(trials))
```

### Comprehension check

Exclude ppts who fail to demonstrate comprehension of the stimulus

```{r}
pre_exclusion <- nrow(trials)

trials = trials %>% filter(rt_trial >= MINIMUM_TRIAL_RT)

print_exclusion_change("Minimum Trial RT", nStart, pre_exclusion, nrow(trials))
```

```{r}
pre_exclusion <- nrow(trials)

trials$description = trimws(trials$description)
trials[is.na(trials$description), ]$description = ""

# remove all empty description responses
trials = trials %>% filter(description != "")

print_exclusion_change("Empty Description Responses", nStart, pre_exclusion, nrow(trials))
```

### Manipulation Identification check

Flag all responses to the purpose identification question that include at least one of several critical keywords.

```{r}
keywords = c("metaphor", "metaphors", "framing", "manipulate", "manipulates", "manipulated", "manipulating", "worded", "wording", "phrased", "phrasing", "measure", "measuring", "measured", "journey", "battle", "path", "fight", "road", "fighting", "fought")

purpose_flag = function(text) {
  # lowercase
  t = tolower(text)
  # remove all punctuation and extra spacing from the text
  t = gsub('[[:punct:] ]+', ' ', t)
  # return a string of the keywords mentioned in the reponse
  return(paste(intersect(keywords, strsplit(t, " ")[[1]]), collapse = ","))
}

# each participant now has a column with any keywords they mentioned
trials$purpose_flag = sapply(trials$purpose, purpose_flag)
```

Manually inspect all responses flagged for ones which identify our metaphor manipulation.

```{r}
trials %>% 
  filter(purpose_flag != "") %>%
  select(ppt, purpose, purpose_flag) %>%
  arrange(purpose_flag)
```

```{r}
pre_exclusion <- nrow(trials)

exclude_ppts = c("hs3taunav6pcbu4uceap", "ogruj45dtbc6h2duxh90")
trials = trials %>% filter(!(ppt %in% exclude_ppts))

print_exclusion_change("Identified Manipulation", nStart, pre_exclusion, nrow(trials))
```

## Final Summary of Exclusions

```{r}
glue("{nrow(trials)} participants remaining")
glue("{nStart - nrow(trials)} participants removed in total")
glue("{round((nStart - nrow(trials)) / nStart,4)*100}% of original participants")
```

## Save Data

```{r}
write_csv(trials, output.file)
```

