---
title: "GoFundMe — Mean Donation"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(gridExtra)
library(glue) # for pretty printing
library(tictoc) # for cell/function profiling
```

## GoFundMe Analysis of Mean Donation

```{r}
projects = read_csv("../../data/processed/gofundme_projects_clean.csv")
projects = within(projects, {
  year = factor(year)
  month = factor(month)
  day_of_week = factor(day_of_week)
})
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma
http://rstudio-pubs-static.s3.amazonaws.com/5691_192685385fc445c9b3fb1619960a20e2.html

# Mean Donation

```{r}
projects %>%
  ggplot() + labs(title="Mean Donation Density") +
  geom_density(aes(mean_donation))
```

```{r}
projects %>%
  ggplot(aes(goal, mean_donation)) + labs(title="Goal Amount Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(duration_float, mean_donation)) + labs(title="Duration Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(text_length_words, mean_donation)) + labs(title="Text Length Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(photos, mean_donation)) + labs(title="Photos Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(updates, mean_donation)) + labs(title="Updates Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(friends, mean_donation)) + labs(title="FB Friends Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(shares, mean_donation)) + labs(title="FB Shares Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(cancer_type, mean_donation)) + labs(title="Cancer Types") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

Establish the base formula to build models off of:

```{r}
base.formula = mean_donation ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,3)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(model.new)$coefficients[key, ])
  cis = confint(model.new, parm=key, method="Wald")
  print(glue("beta: {round(effect[1],3)} (SE: {round(effect[2],3)}) (CI: {round(cis[1],3)}, {round(cis[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 3)}"))
  print(glue("rate ratio: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% (CI: {round((exp(cis[1]*multiplier) - 1)*100,1)}%, {round((exp(cis[2]*multiplier) - 1)*100,1)}%)"))
  print(glue(""))
}
```

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma

Key to interpretation is the log link used here

To put the results from the continuous predictors on interpretable scales, we use a multiplier within the exponent (see `multiplier` in `compare()`). For example, if the multiplier is 1, this leads to: for a one unit increase in this predictor, we see an *x*-fold increase in the DV.

```{r}
# p = function(var, scl=1, digits=6, mult=1.00, mask=T) {
#   mu = mean(projects[mask, ][[var]])
#   sd = sd(projects[mask, ][[var]])
#   print(glue("Var: {var}\t Mean: {round(mu,digits)*scl}\t SD: {round(sd,digits)*scl}\t Scale (x{round(mult, 2)}): {paste(round(mult*sd + mu, digits)*scl)}"))
# }
# p("journey_salience", scl = 1000, digits = 5, mult = 1)
# p("battle_salience", scl = 1000, digits = 5, mult = 0.16)
# p("journey_prod", digits = 4, mask = projects$journey_metaphor > 0)
# p("battle_prod", digits = 4, mask = projects$battle_metaphor > 0)
# p("journey_instantiation", digits = 4, mask = projects$journey_metaphor > 0, mult = 1.6)
# p("battle_instantiation", digits = 4, mask = projects$battle_metaphor > 0, mult = 1.6)
```

## Any Metaphor

Null: The presence of metaphor does not significantly predict the mean donation amount, compared to literal campaigns.

```{r}
projects %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(any_metaphor, mean_donation, fill=any_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects[projects$any_metaphor == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects[projects$any_metaphor, ]$mean_donation), lty=2, color="blue")
```

```{r}
mean.mod.base = glmer(base.formula, data = projects, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r any metaphor}
mod = glmer(update(f,  ~ . + any_metaphor), data = projects, family = Gamma(link = "log"))
compare(mean.mod, mod, "any_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + any_metaphor), data = projects, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "any_metaphorTRUE")
```

## Both Metaphors

Null: The presence of both metaphor families (battle and journey) does not significantly predict the mean donation, compared to literal campaigns.

```{r}
projects.both = projects[projects$no_metaphor | projects$both_metaphor, ] # only projects with both or none
```

N = `r nrow(projects.both)`

```{r}
projects.both %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(both_metaphor, mean_donation, fill=both_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.both[projects.both$both_metaphor == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.both[projects.both$both_metaphor, ]$mean_donation), lty=2, color="blue")
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.both, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.both, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r both metaphors}
mod = glmer(update(f,  ~ . + both_metaphor), data = projects.both, family = Gamma(link = "log"))
compare(mean.mod, mod, "both_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + both_metaphor), data = projects.both, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "both_metaphorTRUE")
```

## Some Metaphor

Null1: Journey metaphors dominating the campaign text does not significantly predict the mean donation, compared to camapigns with only battle metaphors or fewer battle metaphors than journey metaphors.

Null2: Battle metaphors dominating the campaign text does not significantly predict the mean donation, compared to camapigns with only journey metaphors or fewer journey metaphors than battle metaphors.

Null3: Only having the presence of journey metaphors in the campaign text does not significantly predict the mean donation, compared to campaigns with only battle metaphors or a combination of both journey and battle metaphors.

Null4: Only having the presence of battle metaphors in the campaign text does not significantly predict the mean donation, compared to campaigns with only journey metaphors or a combination of both journey and battle metaphors.

```{r}
projects.some = projects[projects$any_metaphor, ]
```
  
N = `r nrow(projects.some)`

```{r}
p1 = projects.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(dom_journey, mean_donation, fill=dom_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some[projects.some$dom_journey == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some[projects.some$dom_journey, ]$mean_donation), lty=2, color="blue")

p2 = projects.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(dom_battle, mean_donation, fill=dom_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some[projects.some$dom_battle == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some[projects.some$dom_battle, ]$mean_donation), lty=2, color="blue")

p3 = projects.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_journey, mean_donation, fill=only_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some[projects.some$only_journey == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some[projects.some$only_journey, ]$mean_donation), lty=2, color="blue")

p4 = projects.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, mean_donation, fill=only_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some[projects.some$only_battle == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some[projects.some$only_battle, ]$mean_donation), lty=2, color="blue")

grid.arrange(p1, p2, p3, p4, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.some, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.some, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r some metaphors reduced}
mod = glmer(update(f,  ~ . + dom_journey), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "dom_journeyTRUE")

mod = glmer(update(f,  ~ . + dom_battle), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "dom_battleTRUE")

mod = glmer(update(f,  ~ . + only_journey), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_journeyTRUE")

mod = glmer(update(f,  ~ . + only_battle), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_battleTRUE")
```

```{r some metaphors full}
mod = glmer(update(base.formula,  ~ . + dom_journey), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "dom_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + dom_battle), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "dom_battleTRUE")

mod = glmer(update(base.formula,  ~ . + only_journey), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_battleTRUE")
```

## Only Journey

Null: Campaigns with only journey metaphors are not significantly more predictive of the mean donation, compared to literal campaigns.

```{r}
projects.some.jor = projects[projects$only_journey | projects$no_metaphor, ]
```

```{r}
nrow(projects.some.jor)
table(projects.some.jor$only_journey)
```

```{r}
cbind(projects.some.jor %>% filter(!only_journey) %>% select(mean_donation) %>% summary(),
      projects.some.jor %>% filter(only_journey) %>% select(mean_donation) %>% summary())

projects.some.jor %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_journey, mean_donation, fill=only_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some.jor[projects.some.jor$only_journey == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some.jor[projects.some.jor$only_journey, ]$mean_donation), lty=2, color="blue")
```

```{r}
mean.mod.base = glmer(base.formula, data = projects.some.jor, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.some.jor, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r only journey}
mod = glmer(update(f,  ~ . + only_journey), data = projects.some.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + only_journey), data = projects.some.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_journeyTRUE")
```

## Journey Modulation

```{r}
projects.jor = projects[projects$journey_metaphor > 0, ]
```

N = `r nrow(projects.jor)`

```{r}
cbind(summary(projects.jor$journey_salience),
      summary(projects.jor$journey_prod),
      summary(projects.jor$journey_instantiation))
```


```{r}
p1 = projects.jor %>%
  ggplot(aes(journey_salience, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="blue")

p2 = projects.jor %>%
  ggplot(aes(journey_prod, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="blue")

p3 = projects.jor %>%
  ggplot(aes(journey_instantiation, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.jor, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - cancer_type)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.jor, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r journey modulation reduced}
mod = glmer(update(f,  ~ . + journey_salience), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "journey_salience")

mod = glmer(update(f,  ~ . + journey_prod), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "journey_prod")

mod = glmer(update(f,  ~ . + journey_instantiation), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "journey_instantiation")
```

```{r journey modulation full}
mod = glmer(update(base.formula,  ~ . + journey_salience), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "journey_salience")

mod = glmer(update(base.formula,  ~ . + journey_prod), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "journey_prod")

mod = glmer(update(base.formula,  ~ . + journey_instantiation), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "journey_instantiation")
```

## Only Battle

Null: Campaigns with only battle metaphors are not significantly more predictive of the mean donation, compared to literal campaigns.

```{r}
projects.some.bat = projects[projects$only_battle | projects$no_metaphor, ]
```

```{r}
nrow(projects.some.bat)
table(projects.some.bat$only_battle)
```

```{r}
cbind(projects.some.bat %>% filter(!only_battle) %>% select(mean_donation) %>% summary(),
      projects.some.bat %>% filter(only_battle) %>% select(mean_donation) %>% summary())

projects.some.bat %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, mean_donation, fill=only_battle)) +
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.some.bat[projects.some.bat$only_battle == F, ]$mean_donation), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.some.bat[projects.some.bat$only_battle, ]$mean_donation), lty=2, color="blue")
```

```{r}
base.formula = mean_donation ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

mean.mod.base = glmer(base.formula, data = projects.some.bat, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.some.bat, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r only battle}
mod = glmer(update(f,  ~ . + only_battle), data = projects.some.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_battleTRUE")

mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.some.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_battleTRUE")
```

## Battle Modulation

```{r}
projects.bat = projects[projects$battle_metaphor > 0, ]
```

N = `r nrow(projects.bat)`

```{r}
cbind(summary(projects.bat$battle_salience),
      summary(projects.bat$battle_prod),
      summary(projects.bat$battle_instantiation))
```

```{r}
p1 = projects.bat %>%
  ggplot(aes(battle_salience, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.bat %>%
  ggplot(aes(battle_prod, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.bat %>%
  ggplot(aes(battle_instantiation, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.bat, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.bat, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r battle modulation reduced}
mod = glmer(update(f,  ~ . + battle_salience), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "battle_salience")

mod = glmer(update(f,  ~ . + battle_prod), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "battle_prod")

mod = glmer(update(f,  ~ . + battle_instantiation), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "battle_instantiation")
```

```{r battle modulation full}
mod = glmer(update(base.formula,  ~ . + battle_salience), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "battle_salience")

mod = glmer(update(base.formula,  ~ . + battle_prod), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "battle_prod")

mod = glmer(update(base.formula,  ~ . + battle_instantiation), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "battle_instantiation")
```
