---
title: "GoFundMe — Status"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(glue)
```

## GoFundMe Analysis of Status

```{r}
projects = read.csv("../../data/processed/gofundme_projects_clean.csv")
projects$month = factor(projects$month)
projects$day_of_week = factor(projects$day_of_week)
```

```{r}
nrow(projects)
```

In total, we have N=5223 IID samples to work with.

```{r}
projects %>%
  ggplot() + labs(title="Goal Amount Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(goal, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="Duration Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(duration_float, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="Text Length Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(text_length_words, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="Photos Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(photos, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="Updates Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(updates, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="FB Friends Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(friends, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="Comments Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(comments, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="FB Shares Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(shares, color=fct_recode(factor(status), "Successful"="1", "Failed"="0"))) +
  theme_minimal()

projects %>%
  ggplot() + labs(title="Cancer Type Counts") + guides(fill=guide_legend(title="Status")) +
  geom_bar(aes(x=cancer_type, fill=fct_recode(factor(status), "Successful"="1", "Failed"="0")), position="dodge") +
  theme(axis.text.x=element_text(angle = 60, hjust=1))

```

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

## Model status

```{r setup base model}
status.formula.base = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

status.mod.base = glmer(status.formula.base, data = projects, family = "binomial")
```

```{r}
# drop1(status.mod.base, test="Chisq")
```

```{r}
status.formula = update(status.formula.base,  ~ . - day_of_week)
# drop1(glmer(status.formula, data = projects, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - month)
# drop1(glmer(status.formula, data = projects, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - text_length_words_sc)
# drop1(glmer(status.formula, data = projects, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - friends_sc)
# drop1(glmer(status.formula, data = projects, family = "binomial"), test="Chisq")
```

The final base model before adding metaphor variables:

```{r create reduced model}
status.mod = glmer(status.formula, data = projects, family = "binomial")
summary(status.mod)
```

## Add metaphors

See https://www.rdocumentation.org/packages/lme4/versions/1.1-19/topics/glmer

https://stats.idre.ucla.edu/other/mult-pkg/faq/general/faq-how-do-i-interpret-odds-ratios-in-logistic-regression/

```{r}
p = function(var, scl=1, digits=6, mult=1.00, mask=T) {
  mu = mean(projects[mask, var])
  sd = sd(projects[mask, var])
  print(glue("Var: {var}\t Mean: {round(mu,digits)*scl}\t SD: {round(sd,digits)*scl}\t Scale (x{round(mult, 2)}): {paste(round(mult*sd + mu, digits)*scl)}"))
}
p("journey_salience", scl = 1000, digits = 5, mult = 0.6)
p("battle_salience", scl = 1000, digits = 5, mult = 0.16)
p("journey_prod", digits = 4, mask = projects$journey_metaphor > 0)
p("battle_prod", digits = 4, mask = projects$battle_metaphor > 0)
p("first_instantiation", digits = 4, mask = projects$journey_metaphor > 0, mult = 1.6)
p("first_instantiation", digits = 4, mask = projects$battle_metaphor > 0, mult = 1.6)
```

```{r}
addMetaphors = function(formula, refit, model) {
  refit(update(formula,  ~ . + any_metaphor), "any_metaphorTRUE", model)
  refit(update(formula,  ~ . + both_metaphor), "both_metaphorTRUE", model)
  refit(update(formula,  ~ . + dom_journey), "dom_journeyTRUE", model)
  refit(update(formula,  ~ . + dom_battle), "dom_battleTRUE", model)
  refit(update(formula,  ~ . + only_battle), "only_battleTRUE", model)
  refit(update(formula,  ~ . + only_journey), "only_journeyTRUE", model)
  refit(update(formula,  ~ . + scale(battle_salience)), "scale(battle_salience)", model, 0.16)
  refit(update(formula,  ~ . + scale(journey_salience)), "scale(journey_salience)", model, 0.6)
}

status.refit = function(formula, key, model, multiplier = 1.0) {
  new.mod = glmer(formula, data = projects, family = "binomial")
  print(anova(new.mod, model, test="Chisq"))
  fe = fixef(new.mod)[key]
  # intercept = fixef(new.mod)["(Intercept)"]
  print(glue("{key}:\t beta: {round(fe,5)}\t odds change: {round((exp(fe*multiplier) - 1)*100, 1)}%"))
}
```

```{r reduced model with metaphor}
addMetaphors(status.formula, status.refit, status.mod)
```

```{r base model with metaphor}
addMetaphors(status.formula.base, status.refit, status.mod.base)
```

## Journey Specific

```{r}
projects.j = projects[projects$journey_metaphor > 0, ]

status.formula.base = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

# status.mod.base = glmer(status.formula.base, data = projects.j, family = "binomial")
```

```{r}
# drop1(status.mod.base, test="Chisq")
```

```{r}
status.formula = update(status.formula.base,  ~ . - friends_sc)
# drop1(glmer(status.formula, data = projects.j, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - day_of_week)
# drop1(glmer(status.formula, data = projects.j, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - text_length_words_sc)
# drop1(glmer(status.formula, data = projects.j, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - cancer_type)
# drop1(glmer(status.formula, data = projects.j, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - duration_float_sc)
# drop1(glmer(status.formula, data = projects.j, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - month)
# drop1(glmer(status.formula, data = projects.j, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(status.formula, data = projects.j, family = "binomial")
summary(status.mod)
```

```{r journey specific}
new.mod = glmer(update(status.formula,  ~ . + journey_prod), data = projects.j, family = "binomial")
print(anova(new.mod, status.mod, test="Chisq"))
fe = fixef(new.mod)["journey_prod"]
print(glue("journey_prod:\t beta: {round(fe,5)}\t odds change: {round((exp(fe) - 1)*100, 1)}%"))

new.mod = glmer(update(status.formula,  ~ . + first_instantiation), data = projects.j, family = "binomial")
print(anova(new.mod, status.mod, test="Chisq"))
fe = fixef(new.mod)["first_instantiation"]
print(glue("first_instantiation:\t beta: {round(fe,5)}\t odds change: {round((exp(fe*1.6) - 1)*100, 1)}%"))
```

## Battle Specific

```{r}
projects.b = projects[projects$battle_metaphor > 0, ]

status.formula.base = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

# status.mod.base = glmer(status.formula.base, data = projects.b, family = "binomial")
```

```{r}
# drop1(status.mod.base, test="Chisq")
```

```{r}
status.formula = update(status.formula.base,  ~ . - friends_sc)
# drop1(glmer(status.formula, data = projects.b, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - text_length_words_sc)
# drop1(glmer(status.formula, data = projects.b, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - day_of_week)
# drop1(glmer(status.formula, data = projects.b, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - month)
# drop1(glmer(status.formula, data = projects.b, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - photos_sc)
# drop1(glmer(status.formula, data = projects.b, family = "binomial"), test="Chisq")
```

```{r}
status.formula = update(status.formula,  ~ . - duration_float_sc)
# drop1(glmer(status.formula, data = projects.b, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(status.formula, data = projects.b, family = "binomial")
summary(status.mod)
```

```{r battle specific}
new.mod = glmer(update(status.formula,  ~ . + battle_prod), data = projects.b, family = "binomial")
print(anova(new.mod, status.mod, test="Chisq"))
fe = fixef(new.mod)["battle_prod"]
print(glue("battle_prod:\t beta: {round(fe,5)}\t odds change: {round((exp(fe) - 1)*100, 1)}%"))

new.mod = glmer(update(status.formula,  ~ . + first_instantiation), data = projects.b, family = "binomial")
print(anova(new.mod, status.mod, test="Chisq"))
fe = fixef(new.mod)["first_instantiation"]
print(glue("first_instantiation:\t beta: {round(fe,5)}\t odds change: {round((exp(fe*1.6) - 1)*100, 1)}%"))
```


