---
title: "GoFundMe — Backers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import libraries

```{r}
library(tidyverse)
library(glmmTMB)
library(glue)
```

## GoFundMe Analysis of Backers

```{r}
projects = read.csv("../../data/processed/gofundme_projects_clean.csv")
projects$month = factor(projects$month)
projects$day_of_week = factor(projects$day_of_week)
```

```{r}
nrow(projects)
```

In total, we have N=5223 IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

# Number of Backers

```{r}
nrow(projects[projects$backers > 1000, ])
ggplot() + labs(x="Number of Backers", title="Number of Backers Density") +
  geom_density(aes(projects$backers[projects$backers < 1000]))
```

We limit to 1000 because removing the outliers leaves us with a nicely shaped distribution.

```{r}
projects.b <- projects[projects$backers < 1000, ]
```

Run a quick data dispersion test (see Rice 1995):

```{r}
s = na.omit(projects.b)
pchisq(2 * sum(projects.b$backers * log(projects.b$backers / mean(projects.b$backers))), length(projects.b$backers) - 1, lower.tail = F)
```

H0: The data are fit well by a Poisson Distribution
H1: Poisson fails to fit the data well

The Poisson distribution obviously does not fit the data well since p approx 0. Let's use a NegBin instead, which can account for differences in the mean and variance.

```{r}
projects.b %>%
  ggplot(aes(goal, backers)) + labs(title="Goal Amount Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.b %>%
  ggplot(aes(duration_float, backers)) + labs(title="Duration Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.b %>%
  ggplot(aes(text_length_words, backers)) + labs(title="Text Length Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.b %>%
  ggplot(aes(photos, backers)) + labs(title="Photos Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.b %>%
  ggplot(aes(updates, backers)) + labs(title="Updates Distribution") +
  geom_point(aes(alpha=0.1)) + 
  theme_minimal()

projects.b %>%
  ggplot(aes(friends, backers)) + labs(title="FB Friends Distribution") +
  geom_point(aes(alpha=0.1)) + 
  theme_minimal()

projects.b %>%
  ggplot(aes(shares, backers)) + labs(title="FB Shares Distribution") +
  geom_point(aes(alpha=0.1)) + 
  theme_minimal()

projects.b %>%
  ggplot(aes(cancer_type, backers)) + labs(title="Cancer Types") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

## Model backers

It might be the case that a quasi-Poisson model fits better, see:
https://digitalcommons.unl.edu/cgi/viewcontent.cgi?article=1141&context=usdeptcommercepub

Here, negative binomial has a lower residual deviance than quasi-poisson. Therefore we use NegBin.

Inherently, the number of backers must be > 0, thus we model using a truncated NegBin fit.

```{r setup base model}
backers.formula.base = backers ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

backers.mod.base = glmmTMB(backers.formula.base, data = projects.b, family = "truncated_nbinom2")
```

```{r}
# drop1(backers.mod.base, test="Chisq")
```

```{r}
backers.formula = update(backers.formula.base,  ~ . - day_of_week)
# drop1(glmmTMB(backers.formula, data = projects.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - friends_sc)
# drop1(glmmTMB(backers.formula, data = projects.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - month)
# drop1(glmmTMB(backers.formula, data = projects.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r create reduced model}
backers.mod = glmmTMB(backers.formula, data = projects.b, family = "truncated_nbinom2")
summary(backers.mod)
```

## Add metaphors

Set up functions used later to simplify metaphor reporting

```{r}
p = function(var, scl=1, digits=6, mult=1.00, mask=T) {
  mu = mean(projects.b[mask, var])
  sd = sd(projects.b[mask, var])
  print(glue("Var: {var}\t Mean: {round(mu,digits)*scl}\t SD: {round(sd,digits)*scl}\t Scale (x{round(mult, 2)}): {paste(round(mult*sd + mu, digits)*scl)}"))
}
p("journey_salience", scl = 1000, digits = 5, mult = 0.6)
p("battle_salience", scl = 1000, digits = 5, mult = 0.16)
p("journey_prod", digits = 4, mask = projects.b$journey_metaphor > 0)
p("battle_prod", digits = 4, mask = projects.b$battle_metaphor > 0)
p("first_instantiation", digits = 4, mask = projects.b$journey_metaphor > 0, mult = 1.6)
p("first_instantiation", digits = 4, mask = projects.b$battle_metaphor > 0, mult = 1.6)
```

```{r}
addMetaphors = function(formula, refit, model) {
  refit(update(formula,  ~ . + any_metaphor), "any_metaphorTRUE", model)
  refit(update(formula,  ~ . + both_metaphor), "both_metaphorTRUE", model)
  refit(update(formula,  ~ . + dom_journey), "dom_journeyTRUE", model)
  refit(update(formula,  ~ . + dom_battle), "dom_battleTRUE", model)
  refit(update(formula,  ~ . + only_battle), "only_battleTRUE", model)
  refit(update(formula,  ~ . + only_journey), "only_journeyTRUE", model)
  refit(update(formula,  ~ . + scale(battle_salience)), "scale(battle_salience)", model, 0.16)
  refit(update(formula,  ~ . + scale(journey_salience)), "scale(journey_salience)", model, 0.6)
}

backers.refit = function(formula, key, model, rr_del = 1.0) {
  new.mod = glmmTMB(formula, data = projects.b, family = "truncated_nbinom2")
  print(anova(new.mod, model, test="Chisq"))
  fe = fixef(new.mod)$cond[key]
  # intercept = fixef(new.mod)$cond["(Intercept)"] \t Intercept: {round(intercept, 5)}
  print(glue("{key}:\t beta: {round(fe,5)}\t rate ratio: {round((exp(fe*rr_del) - 1)*100, 1)}%"))
}
```

```{r reduced model with metaphor}
addMetaphors(backers.formula, backers.refit, backers.mod)
```

Incident Rate Ratio

Projects with any metaphor are expected to have 6.9% more donors than projects with no metaphors at all, with other predictor values remaining constant.


```{r base model with metaphor}
addMetaphors(backers.formula.base, backers.refit, backers.mod.base)
```

## Journey Specific

```{r}
projects.b.j = projects.b[projects.b$journey_metaphor > 0, ]

backers.formula.base = backers ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

# backers.mod.base = glmmTMB(backers.formula.base, data = projects.b.j, family = "truncated_nbinom2")
```

```{r}
# drop1(backers.mod.base, test="Chisq")
```

```{r}
backers.formula = update(backers.formula.base,  ~ . - day_of_week)
# drop1(glmmTMB(backers.formula, data = projects.b.j, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - text_length_words_sc)
# drop1(glmmTMB(backers.formula, data = projects.b.j, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - friends_sc)
# drop1(glmmTMB(backers.formula, data = projects.b.j, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - duration_float_sc)
# drop1(glmmTMB(backers.formula, data = projects.b.j, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - month)
# drop1(glmmTMB(backers.formula, data = projects.b.j, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(backers.formula, data = projects.b.j, family = "truncated_nbinom2")
summary(backers.mod)
```

```{r journey specific}
new.mod = glmmTMB(update(backers.formula,  ~ . + journey_prod), data = projects.b.j, family = "truncated_nbinom2")
print(anova(new.mod, backers.mod, test="Chisq"))
fe = fixef(new.mod)$cond["journey_prod"]
intercept = fixef(new.mod)$cond["(Intercept)"]
print(glue("journey_prod:\t beta: {round(fe,5)}\t Intercept: {round(intercept, 5)}\t rate ratio: {round((exp(fe) - 1)*100, 1)}%"))

new.mod = glmmTMB(update(backers.formula,  ~ . + first_instantiation), data = projects.b.j, family = "truncated_nbinom2")
print(anova(new.mod, backers.mod, test="Chisq"))
fe = fixef(new.mod)$cond["first_instantiation"]
intercept = fixef(new.mod)$cond["(Intercept)"]
print(glue("first_instantiation:\t beta: {round(fe,5)}\t Intercept: {round(intercept, 5)}\t rate ratio: {round((exp(fe*1.6) - 1)*100, 1)}%"))
```

## Battle Specific

```{r}
projects.b.b = projects.b[projects.b$battle_metaphor > 0, ]

backers.formula.base = backers ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

# backers.mod.base = glmmTMB(backers.formula.base, data = projects.b.b, family = "truncated_nbinom2")
```

```{r}
# drop1(backers.mod.base, test="Chisq")
```

```{r}
backers.formula = update(backers.formula.base,  ~ . - month)
# drop1(glmmTMB(backers.formula, data = projects.b.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - friends_sc)
# drop1(glmmTMB(backers.formula, data = projects.b.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - day_of_week)
# drop1(glmmTMB(backers.formula, data = projects.b.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.formula = update(backers.formula,  ~ . - duration_float_sc)
# drop1(glmmTMB(backers.formula, data = projects.b.b, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(backers.formula, data = projects.b.b, family = "truncated_nbinom2")
summary(backers.mod)
```

```{r battle specific}
new.mod = glmmTMB(update(backers.formula,  ~ . + battle_prod), data = projects.b.b, family = "truncated_nbinom2")
print(anova(new.mod, backers.mod, test="Chisq"))
fe = fixef(new.mod)$cond["battle_prod"]
intercept = fixef(new.mod)$cond["(Intercept)"]
print(glue("battle_prod:\t beta: {round(fe,5)}\t Intercept: {round(intercept, 5)}\t rate ratio: {round((exp(fe) - 1)*100, 1)}%"))

new.mod = glmmTMB(update(backers.formula,  ~ . + first_instantiation), data = projects.b.b, family = "truncated_nbinom2")
print(anova(new.mod, backers.mod, test="Chisq"))
fe = fixef(new.mod)$cond["first_instantiation"]
intercept = fixef(new.mod)$cond["(Intercept)"]
print(glue("first_instantiation:\t beta: {round(fe,5)}\t Intercept: {round(intercept, 5)}\t rate ratio: {round((exp(fe*1.6) - 1)*100, 1)}%"))
```

