---
title: "GoFundMe — Mean Donation"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(ggeffects)
library(gridExtra)
library(boot)
library(glue) # for pretty printing
library(tictoc) # for cell/function profiling
```

## GoFundMe Analysis of Mean Donation

```{r}
projects = read_csv("../../data/processed/gofundme_projects_clean.csv")
projects = within(projects, {
  year = factor(year)
  month = factor(month)
  day_of_week = factor(day_of_week)
  any_metaphor = factor(any_metaphor)
  both_metaphor = factor(both_metaphor)
  dom_journey = factor(dom_journey)
  dom_battle = factor(dom_battle)
  only_journey = factor(only_journey)
  only_battle = factor(only_battle)
})
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma
http://rstudio-pubs-static.s3.amazonaws.com/5691_192685385fc445c9b3fb1619960a20e2.html

# Mean Donation

```{r}
projects %>%
  ggplot() + labs(title="Mean Donation Density") +
  geom_density(aes(mean_donation))
```

```{r}
projects %>%
  ggplot(aes(goal, mean_donation)) + labs(title="Goal Amount Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(duration_float, mean_donation)) + labs(title="Duration Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(text_length_words, mean_donation)) + labs(title="Text Length Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(photos, mean_donation)) + labs(title="Photos Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(updates, mean_donation)) + labs(title="Updates Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(friends, mean_donation)) + labs(title="FB Friends Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(shares, mean_donation)) + labs(title="FB Shares Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(cancer_type, mean_donation)) + labs(title="Cancer Types") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

Establish the base formula to build models off of:

```{r}
base.formula = log(mean_donation) ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,3)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(model.new)$coefficients[key, ])
  cis = confint(model.new, parm=key, method="Wald")
  print(glue("beta: {round(effect[1],3)} (SE: {round(effect[2],3)}) (CI: {round(cis[1],3)}, {round(cis[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 3)}"))
  print(glue("rate ratio: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% (CI: {round((exp(cis[1]*multiplier) - 1)*100,1)}%, {round((exp(cis[2]*multiplier) - 1)*100,1)}%)"))
  print(glue(""))
}
```

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma

Key to interpretation is the log link used here

To put the results from the continuous predictors on interpretable scales, we use a multiplier within the exponent (see `multiplier` in `compare()`). For example, if the multiplier is 1, this leads to: for a one unit increase in this predictor, we see an *x*-fold increase in the DV.

## Any Metaphor

Null: The presence of metaphor does not significantly predict the mean donation amount, compared to literal campaigns.

```{r}
projects %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(any_metaphor, mean_donation, fill=any_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects[projects$any_metaphor == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects[projects$any_metaphor, ]$mean_donation), lty=2, color="blue")
```

```{r}
mean.mod.base = lmer(base.formula, data = projects)
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(lmer(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(lmer(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(lmer(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(lmer(f, data = projects), test="Chisq")
```

```{r}
mean.mod = lmer(f, data = projects)
summary(mean.mod)
glue("Coefficients (minus Intercept): ", length(fixef(mean.mod))-1)
```

----

```{r}
base.formula.2 = log(mean_donation) ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + year
mean.mod.base = MASS::rlm(base.formula.2, data = projects)
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula.2,  ~ . - updates_sc)
# drop1(MASS::rlm(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(MASS::rlm(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(MASS::rlm(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(MASS::rlm(f, data = projects), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(MASS::rlm(f, data = projects), test="Chisq")
```

```{r}
rlm.mod = MASS::rlm(update(f, ~ . + any_metaphor), data = projects)
summary(rlm.mod)
```

LASSO model

```{r}
library(glmnet)
```

```{r}
x.vars = model.matrix(update(base.formula.2, ~ . + any_metaphor), projects)
y.var = log(projects$mean_donation)

train = sample(1:nrow(projects), nrow(projects) * 0.75)

cv.out = cv.glmnet(x.vars[train,], y.var[train], alpha = 1.0)

best.lam = cv.out$lambda.min
best.lam
```

```{r}
lasso.mod = glmnet(x.vars[train, ], y.var[train], alpha = 1.0, lambda = best.lam)
pred = predict(lasso.mod, s = best.lam, newx = x.vars)
```

```{r}
sum((y.var - pred)^2)
```

```{r}
coef(lasso.mod)
```

### Results

1239.259

```{r}
sum(resid(mod)^2)
sum(resid(mean.mod)^2)
sum(resid(rlm.mod)^2)
```

```{r}
car::vif(mod)
car::vif(mean.mod)
car::vif(rlm.mod)
```

```{r}
ggplot() +
  geom_qq(aes(sample = resid(mean.mod)), size=0.5) +
  geom_qq_line(aes(sample = resid(mean.mod))) +
  geom_qq(aes(sample = resid(mod)), color="red", size=0.5) +
  geom_qq(aes(sample = resid(rlm.mod)), color="blue", size=0.5)
  # geom_abline(intercept = 0, slope = 1)
  # geom_qq_line(aes(sample = resid(mod)))
```

```{r}
hist(resid(mean.mod))
```

```{r any metaphor}
mod = lmer(update(f,  ~ . + any_metaphor), data = projects)
glue("Coefficients (minus Intercept): ", length(fixef(mod))-1)
# compare(mean.mod, mod, "any_metaphorTRUE")

# any.metaphor.eff = ggpredict(mod, "any_metaphor", type = "re")

# mod = lmer(update(base.formula,  ~ . + any_metaphor), data = projects)
# compare(mean.mod.base, mod, "any_metaphorTRUE")
```


```{r}
f.full = update(f,  ~ . + any_metaphor)
f.full
```

```{r}
r.sq.est = function(data, inds) {
  m0 = lm(log(mean_donation) ~ 1, data = data[inds, ])
  m1 = lmer(f, data = data[inds, ])
  m2 = lmer(f.full, data = data[inds, ])
  
  m0v = summary(m0)$sigma^2
  m1v = summary(m1)$sigma^2
  m2v = summary(m2)$sigma^2
  
  return(((m0v - m2v) / m0v - (m0v - m1v) / m0v) / (1 - (m0v - m2v) / m0v))
}
eta.sq.est = function(data, inds) {
  mod = lmer(f, data = data[inds, ])
  a = anova(mod)
  return(a["any_metaphor", 2] / (sum(a[,2]) + sum(resid(mean.mod)^2)))
}
```

```{r}
tic()
bs.r.sq = boot(projects, r.sq.est, R = 10000, parallel="multicore", ncpus = 3) # 1560.611 sec elapsed
toc()
```

```{r}
plot(bs.r.sq)
bs.r.sq
bc.r.sq = boot.ci(bs.r.sq, type=c("perc", "bca"), conf = 0.95)
bc.r.sq
```

Bootstrap Statistics :
      original       bias    std. error
t1* 0.01105219 0.0001948788 0.002932318
BOOTSTRAP CONFIDENCE INTERVAL CALCULATIONS
Based on 10000 bootstrap replicates

CALL : 
boot.ci(boot.out = bs.r.sq, conf = 0.95, type = c("perc", "bca"))

Intervals : 
Level     Percentile            BCa          
95%   ( 0.0061,  0.0175 )   ( 0.0061,  0.0175 )

```{r}
m2 = lmer(f.full, data = projects)
pwr.f2.test(u = length(fixef(m2)) - 1, v = NULL, f2 = 0.01105219, power = 0.9)
```


```{r}
tic()
bs.eta.sq = boot(projects, eta.sq.est, R = 10000, parallel="multicore", ncpus = 3)
toc()
```

```{r}
plot(bs.eta.sq)
bs.eta.sq
bc.eta.sq = boot.ci(bs.eta.sq, type=c("perc", "bca"), conf = 0.95)
bc.eta.sq
```

Bootstrap Statistics :
      original       bias    std. error
t1* 0.01046683 1.195168e-05 0.002685858

Based on 10000 bootstrap replicates

Intervals : 
Level     Percentile            BCa          
95%   ( 0.0058,  0.0162 )   ( 0.0060,  0.0166 )

```{r}
beta.est = function(data, inds) {
  mod = lmer(f, data = data[inds, ])
  return(fixef(mod)["any_metaphorTRUE"])
}
```

```{r}
# 14.967 minutes

tic()
bs.beta = boot(projects, beta.est, R = 10000, parallel="multicore", ncpus = 3)
toc()
```

```{r}
plot(bs.beta)
bs.beta
bc.beta = boot.ci(bs.beta, type=c("perc", "bca"), conf = 0.95)
bc.beta
```

Bootstrap Statistics :
     original       bias    std. error
t1* 0.1057314 0.0003113569   0.0136496
BOOTSTRAP CONFIDENCE INTERVAL CALCULATIONS
Based on 10000 bootstrap replicates

CALL : 
boot.ci(boot.out = bs.beta, conf = 0.95, type = c("perc", "bca"))

Intervals : 
Level     Percentile            BCa          
95%   ( 0.0789,  0.1324 )   ( 0.0777,  0.1314 ) 


```{r}

# 5*(1+c(bc$basic[4], bc$basic[5])) - 5
# 5*(1+c(bc$percent[4], bc$percent[5])) - 5

# round(12.75*(1+c(bc$basic[4], bc$basic[5])) - 12.75, 2)
round(12.75*(1+c(bc.eta.sq$bca[4], bc.eta.sq$bca[5])) - 12.75, 2)

# 25*(1+c(bc$basic[4], bc$basic[5])) - 25
# 25*(1+c(bc$percent[4], bc$percent[5])) - 25
```

## Both Metaphors

Null: The presence of both metaphor families (battle and journey) does not significantly predict the mean donation, compared to literal campaigns.

```{r}
projects.both = projects[projects$no_metaphor == "TRUE" | projects$both_metaphor == "TRUE", ] # only projects with both or none
```

N = `r nrow(projects.both)`

```{r}
projects.both %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(both_metaphor, mean_donation, fill=both_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.both[projects.both$both_metaphor == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.both[projects.both$both_metaphor, ]$mean_donation), lty=2, color="blue")
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = lmer(base.formula, data = projects.both)
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - .)
# drop1(lmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - .)
# drop1(lmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

...

```{r}
# f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
# f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
# f = update(f,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.both, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r both metaphors}
mod = glmer(update(f,  ~ . + both_metaphor), data = projects.both, family = Gamma(link = "log"))
compare(mean.mod, mod, "both_metaphorTRUE")

both.metaphor.eff = ggpredict(mod, "both_metaphor", type = "re")

mod = glmer(update(base.formula,  ~ . + both_metaphor), data = projects.both, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "both_metaphorTRUE")
```

## Compared Metaphor

Null1: Only using battle metaphors within the campaign text does not significantly predict the mean donation, compared to campaigns which only use journey metaphors

```{r}
projects.comp = projects[projects$any_metaphor == "TRUE" & projects$both_metaphor == "FALSE", ]
```

N = `r nrow(projects.comp)`

```{r}
cbind(projects.comp %>% filter(only_battle == "FALSE") %>% select(mean_donation) %>% summary(),
      projects.comp %>% filter(only_battle == "TRUE") %>% select(mean_donation) %>% summary())
```


```{r}
projects.comp %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, mean_donation, fill=only_battle)) +
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some[projects.some$only_battle == "TRUE", ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some[projects.some$only_battle == "FALSE", ]$mean_donation), lty=2, color="blue")
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.comp, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.comp, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.comp, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.comp, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.comp, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.comp, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r some metaphors reduced}
mod = glmer(update(f,  ~ . + only_battle), data = projects.comp, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_battleTRUE")

comp.eff = ggpredict(mod, "only_battle", type = "re")
```

```{r some metaphors full}
mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.comp, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_battleTRUE")
```

## Only Journey

Null: Campaigns with only journey metaphors are not significantly more predictive of the mean donation, compared to literal campaigns.

```{r}
projects.some.jor = projects[projects$only_journey == "TRUE" | projects$no_metaphor == "TRUE", ]
```

```{r}
nrow(projects.some.jor)
table(projects.some.jor$only_journey)
```

```{r}
cbind(projects.some.jor %>% filter(only_journey == "FALSE") %>% select(mean_donation) %>% summary(),
      projects.some.jor %>% filter(only_journey == "TRUE") %>% select(mean_donation) %>% summary())

projects.some.jor %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_journey, mean_donation, fill=only_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some.jor[projects.some.jor$only_journey == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some.jor[projects.some.jor$only_journey, ]$mean_donation), lty=2, color="blue")
```

```{r}
mean.mod.base = glmer(base.formula, data = projects.some.jor, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.some.jor, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r only journey}
mod = glmer(update(f,  ~ . + only_journey), data = projects.some.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_journeyTRUE")

only.journey.eff = ggpredict(mod, "only_journey", type = "re")

mod = glmer(update(base.formula,  ~ . + only_journey), data = projects.some.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_journeyTRUE")
```

## Journey Modulation

```{r}
projects.jor = projects[projects$journey_metaphor > 0, ]
```

N = `r nrow(projects.jor)`

```{r}
cbind(summary(projects.jor$journey_salience),
      summary(projects.jor$journey_rare),
      summary(projects.jor$journey_early))
```


```{r}
p1 = projects.jor %>%
  ggplot(aes(journey_salience, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="blue")

p2 = projects.jor %>%
  ggplot(aes(journey_rare, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="blue")

p3 = projects.jor %>%
  ggplot(aes(journey_early, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.jor, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - cancer_type)
# drop1(glmer(f, data = projects.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.jor, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r journey modulation reduced}
mod = glmer(update(f,  ~ . + journey_salience), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "journey_salience")

journey.salience.eff = ggpredict(mod, "journey_salience", type = "re")

mod = glmer(update(f,  ~ . + journey_rare), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "journey_rare")

journey.rare.eff = ggpredict(mod, "journey_rare", type = "re")

mod = glmer(update(f,  ~ . + journey_early), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "journey_early")

journey.early.eff = ggpredict(mod, "journey_early", type = "re")
```

```{r journey modulation full}
mod = glmer(update(base.formula,  ~ . + journey_salience), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "journey_salience")

mod = glmer(update(base.formula,  ~ . + journey_rare), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "journey_rare")

mod = glmer(update(base.formula,  ~ . + journey_early), data = projects.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "journey_early")
```

## Only Battle

Null: Campaigns with only battle metaphors are not significantly more predictive of the mean donation, compared to literal campaigns.

```{r}
projects.some.bat = projects[projects$only_battle == "TRUE" | projects$no_metaphor == "TRUE", ]
```

```{r}
nrow(projects.some.bat)
table(projects.some.bat$only_battle)
```

```{r}
cbind(projects.some.bat %>% filter(only_battle == "FALSE") %>% select(mean_donation) %>% summary(),
      projects.some.bat %>% filter(only_battle == "TRUE") %>% select(mean_donation) %>% summary())

projects.some.bat %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, mean_donation, fill=only_battle)) +
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.some.bat[projects.some.bat$only_battle == F, ]$mean_donation), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.some.bat[projects.some.bat$only_battle, ]$mean_donation), lty=2, color="blue")
```

```{r}
mean.mod.base = glmer(base.formula, data = projects.some.bat, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.some.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.some.bat, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r only battle}
mod = glmer(update(f,  ~ . + only_battle), data = projects.some.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_battleTRUE")

only.battle.eff = ggpredict(mod, "only_battle", type = "re")

mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.some.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_battleTRUE")
```

## Battle Modulation

```{r}
projects.bat = projects[projects$battle_metaphor > 0, ]
```

N = `r nrow(projects.bat)`

```{r}
cbind(summary(projects.bat$battle_salience),
      summary(projects.bat$battle_rare),
      summary(projects.bat$battle_early))
```

```{r}
p1 = projects.bat %>%
  ggplot(aes(battle_salience, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.bat %>%
  ggplot(aes(battle_rare, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.bat %>%
  ggplot(aes(battle_early, mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

```{r}
projects[projects$mean_donation > 3000, ]
```


Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.bat, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.bat, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r battle modulation reduced}
mod = glmer(update(f,  ~ . + battle_salience), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "battle_salience")

battle.salience.eff = ggpredict(mod, "battle_salience", type = "re")

mod = glmer(update(f,  ~ . + battle_rare), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "battle_rare")

battle.rare.eff = ggpredict(mod, "battle_rare", type = "re")

mod = glmer(update(f,  ~ . + battle_early), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "battle_early")

battle.early.eff = ggpredict(mod, "battle_early", type = "re")
```

```{r battle modulation full}
mod = glmer(update(base.formula,  ~ . + battle_salience), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "battle_salience")

mod = glmer(update(base.formula,  ~ . + battle_rare), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "battle_rare")

mod = glmer(update(base.formula,  ~ . + battle_early), data = projects.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "battle_early")
```

# Effect Visualization

```{r}
t = theme_minimal() + theme(
  text = element_text(family = "Times"),
  plot.title = element_text(size=9),
  axis.text = element_text(size = 9),
  axis.title = element_text(size = 9),
  legend.text = element_text(size = 9),
  legend.title = element_text(size = 9),
  panel.grid.minor.y = element_blank())
```

```{r}
any.metaphor.eff$var = 'Any Metaphor***'
both.metaphor.eff$var = 'Both Metaphors**'
comp.eff$var = 'Only Battle (A)'
only.battle.eff$var = 'Only Battle (B)***'
only.journey.eff$var = 'Only Journey**'

ps = data.frame(x = rep(1.5,5), 
                y = rep(105, 5),
                t = c("***","**","","***","**"),
                var = c("Any\nMetaphor", "Both\nMetaphors", "Only\nBattle (A)", "Only\nBattle (B)", "Only\nJourney"))

viz = any.metaphor.eff %>% 
  bind_rows(both.metaphor.eff) %>%
  bind_rows(comp.eff) %>%
  bind_rows(only.battle.eff) %>%
  bind_rows(only.journey.eff) %>%
  ggplot() + t +
  facet_grid(rows = vars(var)) +
  geom_path(aes(x, predicted, group=1), linetype=2, size=0.5, color="#888888") +
  geom_point(aes(x, predicted, color=x)) +
  geom_errorbar(aes(x, predicted, ymin = conf.low, ymax = conf.high, color=x), size=0.5, width = 0.1) +
  scale_color_manual(breaks=c("FALSE", "TRUE"), values=c("#AE2E11", "#F56F51")) +
  scale_y_continuous(labels = scales::dollar) +
  theme(legend.position = "none") +
  geom_text(aes(x, y, label=t), data = ps) +
  labs(x = "Subset", y = "Mean Donation", title = "Estimated marginal prediction intervals\nfor Mean Donation")

viz
ggsave("discr_effects.png", viz, height = 4.25, width = 3.25)
```


```{r}
viz = any.metaphor.eff %>%
  
  ggplot() + t +
  geom_path(aes(x, predicted, group=1), linetype=1, size=0.5) +
  geom_point(aes(x, predicted)) +
  geom_errorbar(aes(x, predicted, ymin = conf.low, ymax = conf.high), size=0.5, width = 0.1) +
  scale_y_continuous(labels = scales::dollar) +
  theme(axis.title.x = element_blank()) +
  scale_x_discrete(labels = c("FALSE"="No Metaphor", "TRUE"="Any Metaphor")) +
  scale_color_grey() +
  labs(y = "Mean Donation", title = "Marginal prediction intervals for Any Metaphor")

viz
ggsave("discr_effects3.png", viz, height = 1.6, width = 3, dpi = 300)
```

```{r}
battle.salience.eff$var = "Salience"
battle.rare.eff$var = "Rarity"
battle.early.eff$var = "Earliness"
journey.salience.eff$var = "Salience"
journey.rare.eff$var = "Rarity"
journey.early.eff$var = "Earliness"

battle.salience.eff$fam = "Battle"
battle.rare.eff$fam = "Battle"
battle.early.eff$fam = "Battle"
journey.salience.eff$fam = "Journey"
journey.rare.eff$fam = "Journey"
journey.early.eff$fam = "Journey"

# ps = data.frame(x = rep(1.5,6), 
#                 y = rep(110, 6),
#                 t = c("***","***","","","*","*"))

viz = battle.salience.eff %>% 
  bind_rows(battle.rare.eff) %>%
  bind_rows(battle.early.eff) %>% 
  bind_rows(journey.salience.eff) %>% 
  bind_rows(journey.rare.eff) %>%
  bind_rows(journey.early.eff) %>%
  ggplot() + t +
  facet_grid(. ~ var, scales = "free") +
  geom_ribbon(aes(x, ymin = conf.low, ymax = conf.high, fill=fam), alpha = 0.2) +
  geom_line(aes(x, predicted, color=fam)) +
  # theme(legend.title = element_text("Metaphor Family")) +
  # geom_text(aes(x, y, label=t), data = ps) +
  labs(x = "SDs", y = "Predicted Mean Donation", title = "Predicted Mean Donation for\n each Predictor of Interest")

viz
ggsave("cont_effects.png", viz, height = 4, width = 5)
```
