---
title: "GoFundMe — Status"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(gridExtra)
library(glue) # for pretty printing
```

## GoFundMe Analysis of Status

```{r}
projects = read.csv("../../data/processed/gofundme_projects_clean.csv")
projects$year = factor(projects$year)
projects$month = factor(projects$month)
projects$day_of_week = factor(projects$day_of_week)
projects$status = factor(projects$status)
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

# Status

```{r}
th = theme_minimal()
projects %>%
  ggplot() + th + labs(title="Goal Amount Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(goal, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Duration Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(duration_float, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Text Length Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(text_length_words, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Photos Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(photos, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Updates Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(updates, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="FB Friends Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(friends, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Comments Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(comments, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="FB Shares Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(shares, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Cancer Type Counts") + guides(fill=guide_legend(title="Status")) +
  geom_bar(aes(x=cancer_type, fill=fct_recode(factor(status), "Successful"="1", "Failed"="0")), position="dodge") +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

Establish the base formula to build models off of:

```{r}
base.formula = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t New AIC: {round(a$AIC[2], 1)}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,4)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(mod)$coefficients[key, ])
  print(glue("beta: {round(effect[1],4)} (+/- {round(effect[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 4)}"))
  print(glue("odds change: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% ({round((exp((effect[1] - effect[2])*multiplier) - 1)*100, 1)}% to {round((exp((effect[1] + effect[2])*multiplier) - 1)*100, 1)}%)"))
  print(glue(""))
}
```

To put the results from the continuous predictors on interpretable scales, we use a multiplier within the exponent (see `factor` in `compare()`). For example, if the multiplier is 1, this leads to: for a one unit increase in this predictor, we see an *x*-fold increase in the DV.

```{r}
p = function(var, scl=1, digits=6, mult=1.00, mask=T) {
  mu = mean(projects[mask, var])
  sd = sd(projects[mask, var])
  print(glue("Var: {var}\t Mean: {round(mu,digits)*scl}\t SD: {round(sd,digits)*scl}\t Scale (x{round(mult, 2)}): {paste(round(mult*sd + mu, digits)*scl)}"))
}
p("journey_salience", scl = 1000, digits = 5, mult = 0.6)
p("battle_salience", scl = 1000, digits = 5, mult = 0.16)
p("journey_prod", digits = 4, mask = projects$journey_metaphor > 0)
p("battle_prod", digits = 4, mask = projects$battle_metaphor > 0)
p("first_instantiation", digits = 4, mask = projects$journey_metaphor > 0, mult = 1.6)
p("first_instantiation", digits = 4, mask = projects$battle_metaphor > 0, mult = 1.6)
```

## Any Metaphor

Examine: does having any instance of metaphor influence status?

Null: having any metaphor is not significantly different from having no metaphor

```{r}
projects %>%
  ggplot() + th + geom_bar(aes(status, fill=any_metaphor), position="dodge")
```

```{r}
status.mod.base = glmer(base.formula, data = projects, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects, family = "binomial")
summary(status.mod)
```

### Results

```{r any metaphor}
mod = glmer(update(f,  ~ . + any_metaphor), data = projects, family = "binomial")
compare(status.mod, mod, "any_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + any_metaphor), data = projects, family = "binomial")
compare(status.mod.base, mod, "any_metaphorTRUE")
```

## Both Metaphors

Examine: does having both metaphor families present influence status?

Null: having both metaphor families is not significantly different from having no metaphor

```{r}
projects.both = projects[(1-projects$any_metaphor) | projects$both_metaphor, ] # only projects with both or none
```

N = `r nrow(projects.both)`

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.both, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.both, family = "binomial")
# summary(status.mod)
```

### Results

```{r both metaphors}
mod = glmer(update(f,  ~ . + both_metaphor), data = projects.both, family = "binomial")
compare(status.mod, mod, "both_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + both_metaphor), data = projects.both, family = "binomial")
compare(status.mod.base, mod, "both_metaphorTRUE")
```

## Some Metaphor

Examine: does having only journey/battle, or dominant journey/battle, influence status?

Null: having only journey/battle, or dominant journey/battle, is not significantly different from negative

```{r}
projects.some = projects[projects$any_metaphor, ]
```

N = `r nrow(projects.some)`

```{r}
projects.some %>%
  group_by(status, dom_journey) %>%
  summarize(n = n())
```


```{r fig.width=8}
p1 = projects.some %>%
  ggplot() + th +
  geom_bar(aes(status, fill=dom_journey), position = "dodge") + 
  lims(y=c(0,2500)) + labs(title="Dominant Journey")

p2 = projects.some %>%
  ggplot() + th +
  geom_bar(aes(status, fill=dom_battle), position = "dodge") +
  lims(y=c(0,2500)) + labs(title="Dominant Battle")

p3 = projects.some %>%
  ggplot() + th +
  geom_bar(aes(status, fill=only_journey), position = "dodge") +
  lims(y=c(0,2500)) + labs(title="Only Journey")

p4 = projects.some %>%
  ggplot() + th +
  geom_bar(aes(status, fill=only_battle), position = "dodge") +
  lims(y=c(0,2500)) + labs(title="Only Battle")

grid.arrange(p1, p2, p3, p4, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.some, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.some, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.some, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.some, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.some, family = "binomial")
# summary(status.mod)
```

### Results

```{r some metaphors reduced}
mod = glmer(update(f,  ~ . + dom_journey), data = projects.some, family = "binomial")
compare(status.mod, mod, "dom_journeyTRUE")

mod = glmer(update(f,  ~ . + dom_battle), data = projects.some, family = "binomial")
compare(status.mod, mod, "dom_battleTRUE")

mod = glmer(update(f,  ~ . + only_journey), data = projects.some, family = "binomial")
compare(status.mod, mod, "only_journeyTRUE")

mod = glmer(update(f,  ~ . + only_battle), data = projects.some, family = "binomial")
compare(status.mod, mod, "only_battleTRUE")
```

```{r some metaphors full}
mod = glmer(update(base.formula,  ~ . + dom_journey), data = projects.some, family = "binomial")
compare(status.mod.base, mod, "dom_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + dom_battle), data = projects.some, family = "binomial")
compare(status.mod.base, mod, "dom_battleTRUE")

mod = glmer(update(base.formula,  ~ . + only_journey), data = projects.some, family = "binomial")
compare(status.mod.base, mod, "only_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.some, family = "binomial")
compare(status.mod.base, mod, "only_battleTRUE")
```

## Journey

```{r}
projects.jor = projects[projects$journey_metaphor > 0, ]
```

N = `r nrow(projects.jor)`

```{r}
p1 = projects.jor %>%
  ggplot() + th +
  geom_violin(aes(status, journey_salience, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$journey_salience), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$journey_salience), lty=2, color="blue")

p2 = projects.jor %>%
  ggplot() + th +
  geom_violin(aes(status, journey_prod, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$journey_prod), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$journey_prod), lty=2, color="blue")

p3 = projects.jor %>%
  ggplot() + th +
  geom_violin(aes(status, first_instantiation, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$first_instantiation), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$first_instantiation), lty=2, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.jor, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - cancer_type)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.jor, family = "binomial")
# summary(status.mod)
```

### Results

```{r journey specific reduced}
mod = glmer(update(f,  ~ . + scale(journey_salience)), data = projects.jor, family = "binomial")
compare(status.mod, mod, "scale(journey_salience)", 0.6)

mod = glmer(update(f,  ~ . + scale(journey_prod)), data = projects.jor, family = "binomial")
compare(status.mod, mod, "scale(journey_prod)")

mod = glmer(update(f,  ~ . + scale(first_instantiation)), data = projects.jor, family = "binomial")
compare(status.mod, mod, "scale(first_instantiation)")
```

```{r journey specific full}
mod = glmer(update(base.formula,  ~ . + scale(journey_salience)), data = projects.jor, family = "binomial")
compare(status.mod.base, mod, "scale(journey_salience)", 0.6)

mod = glmer(update(base.formula,  ~ . + scale(journey_prod)), data = projects.jor, family = "binomial")
compare(status.mod.base, mod, "scale(journey_prod)")

mod = glmer(update(base.formula,  ~ . + scale(first_instantiation)), data = projects.jor, family = "binomial")
compare(status.mod.base, mod, "scale(first_instantiation)")
```

## Battle

```{r}
projects.bat = projects[projects$battle_metaphor > 0, ]
```

N = `r nrow(projects.bat)`

```{r}
p1 = projects.bat %>%
  ggplot() + th +
  geom_violin(aes(status, battle_salience, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$battle_salience), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$battle_salience), lty=2, color="blue")

p2 = projects.bat %>%
  ggplot() + th +
  geom_violin(aes(status, battle_prod, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$battle_prod), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$battle_prod), lty=2, color="blue")

p3 = projects.bat %>%
  ggplot() + th +
  geom_violin(aes(status, first_instantiation, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$first_instantiation), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$first_instantiation), lty=2, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.bat, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.bat, family = "binomial")
# summary(status.mod)
```

### Results

```{r battle specific reduced}
mod = glmer(update(f,  ~ . + scale(battle_salience)), data = projects.bat, family = "binomial")
compare(status.mod, mod, "scale(battle_salience)", 0.16)

mod = glmer(update(f,  ~ . + scale(battle_prod)), data = projects.bat, family = "binomial")
compare(status.mod, mod, "scale(battle_prod)")

mod = glmer(update(f,  ~ . + scale(first_instantiation)), data = projects.bat, family = "binomial")
compare(status.mod, mod, "scale(first_instantiation)")
```

```{r battle specific full}
mod = glmer(update(base.formula,  ~ . + scale(battle_salience)), data = projects.bat, family = "binomial")
compare(status.mod.base, mod, "scale(battle_salience)", 0.16)

mod = glmer(update(base.formula,  ~ . + scale(battle_prod)), data = projects.bat, family = "binomial")
compare(status.mod.base, mod, "scale(battle_prod)")

mod = glmer(update(base.formula,  ~ . + scale(first_instantiation)), data = projects.bat, family = "binomial")
compare(status.mod.base, mod, "scale(first_instantiation)")
```

## Without RE

```{r}
base.formula = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + year
```

```{r}
status.mod.base = glm(base.formula, data = projects, family = "binomial")
drop1(status.mod.base, test="Chisq")
```

```{r}
summary(status.mod.base)
```


```{r}
f = update(base.formula,  ~ . - duration_float_sc)
drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
summary(glm(f, data = projects, family = "binomial"))
```

