---
title: "GoFundMe — Backers"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(glmmTMB)
library(gridExtra)
library(glue) # for pretty printing
library(tictoc) # for cell/function profiling
```

## GoFundMe Analysis of Backers

```{r}
projects = read.csv("../../data/processed/gofundme_projects_clean.csv")
projects$month = factor(projects$month)
projects$day_of_week = factor(projects$day_of_week)
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

# Backers

```{r}
upper_limit = quantile(projects$backers, 0.995)
nrow(projects[projects$backers > upper_limit, ])
projects.trunc = projects[projects$backers < upper_limit, ]

ggplot() + labs(x="Number of Backers", title="Number of Backers Density") +
  geom_density(aes(projects$backers[projects$backers < upper_limit]))
```

Run a quick data dispersion test (see Rice 1995):

```{r}
s = na.omit(projects.trunc)
pchisq(2 * sum(projects.trunc$backers * log(projects.trunc$backers / mean(projects.trunc$backers))), length(projects.trunc$backers) - 1, lower.tail = F)
```

H0: The data are fit well by a Poisson Distribution
H1: Poisson fails to fit the data well

The Poisson distribution obviously does not fit the data well since p approx 0. Let's use a NegBin instead, which can account for differences in the mean and variance.

```{r}
projects.trunc %>%
  ggplot(aes(goal, backers)) + labs(title="Goal Amount Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(duration_float, backers)) + labs(title="Duration Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(text_length_words, backers)) + labs(title="Text Length Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(photos, backers)) + labs(title="Photos Distribution") +
  geom_point(aes(alpha=0.1)) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(updates, backers)) + labs(title="Updates Distribution") +
  geom_point(aes(alpha=0.1)) + 
  theme_minimal()

projects.trunc %>%
  ggplot(aes(friends, backers)) + labs(title="FB Friends Distribution") +
  geom_point(aes(alpha=0.1)) + 
  theme_minimal()

projects.trunc %>%
  ggplot(aes(shares, backers)) + labs(title="FB Shares Distribution") +
  geom_point(aes(alpha=0.1)) + 
  theme_minimal()

projects.trunc %>%
  ggplot(aes(cancer_type, backers)) + labs(title="Cancer Types") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

Establish the base formula to build models off of:

```{r}
base.formula = backers ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t New AIC: {round(a$AIC[2], 1)}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,4)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(mod)$coefficients$cond[key, ])
  print(glue("beta: {round(effect[1],4)} (+/- {round(effect[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 4)}"))
  print(glue("rate ratio: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% ({round((exp((effect[1] - effect[2])*multiplier) - 1)*100, 1)}% to {round((exp((effect[1] + effect[2])*multiplier) - 1)*100, 1)}%)"))
  print(glue(""))
}
```

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma

Key to interpretation is the log link used here

To put the results from the continuous predictors on interpretable scales, we use a multiplier within the exponent (see `factor` in `compare()`). For example, if the multiplier is 1, this leads to: for a one unit increase in this predictor, we see an *x*-fold increase in the DV.

```{r}
p = function(var, scl=1, digits=6, mult=1.00, mask=T) {
  mu = mean(projects[mask, var])
  sd = sd(projects[mask, var])
  print(glue("Var: {var}\t Mean: {round(mu,digits)*scl}\t SD: {round(sd,digits)*scl}\t Scale (x{round(mult, 2)}): {paste(round(mult*sd + mu, digits)*scl)}"))
}
p("journey_salience", scl = 1000, digits = 5, mult = 0.6)
p("battle_salience", scl = 1000, digits = 5, mult = 0.16)
p("journey_prod", digits = 4, mask = projects$journey_metaphor > 0)
p("battle_prod", digits = 4, mask = projects$battle_metaphor > 0)
p("first_instantiation", digits = 4, mask = projects$journey_metaphor > 0, mult = 1.6)
p("first_instantiation", digits = 4, mask = projects$battle_metaphor > 0, mult = 1.6)
```

It might be the case that a quasi-Poisson model fits better, see:
https://digitalcommons.unl.edu/cgi/viewcontent.cgi?article=1141&context=usdeptcommercepub

Here, negative binomial has a lower residual deviance than quasi-poisson. Therefore we use NegBin.

Inherently, the number of backers must be > 0, thus we model using a truncated NegBin fit.

The coefficients of each model can be exponentiated to get the Incident Rate Ratio. 

An example rationalization would look like: *Projects with any metaphor are expected to have 5.0% more donors than projects with no metaphors at all, with other predictor values remaining constant.*

## Any Metaphor

Examine: does having any instance of metaphor influence backers?

Null: having any metaphor is not significantly different from having no metaphor

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.trunc, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.trunc, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.trunc, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects.trunc, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.trunc, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r any metaphor}
mod = glmmTMB(update(f,  ~ . + any_metaphor), data = projects.trunc, family = "truncated_nbinom2")
compare(backers.mod, mod, "any_metaphorTRUE")

# mod = glmmTMB(update(base.formula,  ~ . + any_metaphor), data = projects.trunc, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "any_metaphorTRUE")
```

## Both Metaphors

Examine: does having both metaphor families present influence backers?

Null: having both metaphor families is not significantly different from having no metaphor

```{r}
projects.trunc.both = projects.trunc[(1-projects.trunc$any_metaphor) | projects.trunc$both_metaphor, ] # only projects with both or none
```

N = `r nrow(projects.trunc.both)`

```{r}
projects.trunc.both %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(both_metaphor, backers, fill=both_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.both[projects.trunc.both$both_metaphor == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.both[projects.trunc.both$both_metaphor, ]$backers), lty=2, color="blue")

```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.trunc.both, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.trunc.both, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.trunc.both, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r both metaphors}
mod = glmmTMB(update(f,  ~ . + both_metaphor), data = projects.trunc.both, family = "truncated_nbinom2")
compare(backers.mod, mod, "both_metaphorTRUE")

# mod = glmmTMB(update(base.formula,  ~ . + both_metaphor), data = projects.trunc.both, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "both_metaphorTRUE")
```

## Some Metaphor

Examine: does having only journey/battle, or dominant journey/battle, influence backers?

Null: having only journey/battle, or dominant journey/battle, is not significantly different from negative

```{r}
projects.trunc.some = projects.trunc[projects.trunc$any_metaphor, ]
```

N = `r nrow(projects.trunc.some)`

```{r}
p1 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(dom_journey, backers, fill=dom_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_journey == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_journey, ]$backers), lty=2, color="blue")

p2 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(dom_battle, backers, fill=dom_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_battle == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_battle, ]$backers), lty=2, color="blue")

p3 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_journey, backers, fill=only_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_journey == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_journey, ]$backers), lty=2, color="blue")

p4 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, backers, fill=only_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_battle == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_battle, ]$backers), lty=2, color="blue")

grid.arrange(p1, p2, p3, p4, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.trunc.some, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmmTMB(f, data = projects.trunc.some, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.trunc.some, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.trunc.some, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmmTMB(f, data = projects.trunc.some, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.trunc.some, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r some metaphors reduced}
mod = glmmTMB(update(f,  ~ . + dom_journey), data = projects.trunc.some, family = "truncated_nbinom2")
compare(backers.mod, mod, "dom_journeyTRUE")

mod = glmmTMB(update(f,  ~ . + dom_battle), data = projects.trunc.some, family = "truncated_nbinom2")
compare(backers.mod, mod, "dom_battleTRUE")

mod = glmmTMB(update(f,  ~ . + only_journey), data = projects.trunc.some, family = "truncated_nbinom2")
compare(backers.mod, mod, "only_journeyTRUE")

mod = glmmTMB(update(f,  ~ . + only_battle), data = projects.trunc.some, family = "truncated_nbinom2")
compare(backers.mod, mod, "only_battleTRUE")
```

```{r some metaphors full}
# mod = glmmTMB(update(base.formula,  ~ . + dom_journey), data = projects.trunc.some, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "dom_journeyTRUE")
# 
# mod = glmmTMB(update(base.formula,  ~ . + dom_battle), data = projects.trunc.some, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "dom_battleTRUE")
# 
# mod = glmmTMB(update(base.formula,  ~ . + only_journey), data = projects.trunc.some, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "only_journeyTRUE")
# 
# mod = glmmTMB(update(base.formula,  ~ . + only_battle), data = projects.trunc.some, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "only_battleTRUE")
```

## Journey

```{r}
projects.trunc.jor = projects.trunc[projects.trunc$journey_metaphor > 0, ]
```

N = `r nrow(projects.trunc.jor)`

```{r}
p1 = projects.trunc.jor %>%
  ggplot(aes(scale(journey_salience), backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.trunc.jor %>%
  ggplot(aes(scale(journey_prod), backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.trunc.jor %>%
  ggplot(aes(scale(first_instantiation), backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.trunc.jor, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.trunc.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmmTMB(f, data = projects.trunc.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.trunc.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmmTMB(f, data = projects.trunc.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects.trunc.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.trunc.jor, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r journey specific reduced}
mod = glmmTMB(update(f,  ~ . + scale(journey_salience)), data = projects.trunc.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "scale(journey_salience)", 0.6)

mod = glmmTMB(update(f,  ~ . + scale(journey_prod)), data = projects.trunc.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "scale(journey_prod)")

mod = glmmTMB(update(f,  ~ . + scale(first_instantiation)), data = projects.trunc.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "scale(first_instantiation)")
```

```{r journey specific full}
# mod = glmmTMB(update(base.formula,  ~ . + scale(journey_salience)), data = projects.trunc.jor, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "scale(journey_salience)", 0.6)
# 
# mod = glmmTMB(update(base.formula,  ~ . + scale(journey_prod)), data = projects.trunc.jor, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "scale(journey_prod)")
# 
# mod = glmmTMB(update(base.formula,  ~ . + scale(first_instantiation)), data = projects.trunc.jor, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "scale(first_instantiation)")
```

## Battle

```{r}
projects.trunc.bat = projects.trunc[projects.trunc$battle_metaphor > 0, ]
```

N = `r nrow(projects.trunc.bat)`

```{r}
p1 = projects.trunc.bat %>%
  ggplot(aes(scale(battle_salience), backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.trunc.bat %>%
  ggplot(aes(scale(battle_prod), backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.trunc.bat %>%
  ggplot(aes(scale(first_instantiation), backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.trunc.bat, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmmTMB(f, data = projects.trunc.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.trunc.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.trunc.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmmTMB(f, data = projects.trunc.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.trunc.bat, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r battle specific reduced}
mod = glmmTMB(update(f,  ~ . + scale(battle_salience)), data = projects.trunc.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "scale(battle_salience)", 0.16)

mod = glmmTMB(update(f,  ~ . + scale(battle_prod)), data = projects.trunc.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "scale(battle_prod)")

mod = glmmTMB(update(f,  ~ . + scale(first_instantiation)), data = projects.trunc.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "scale(first_instantiation)")
```

```{r battle specific full}
# mod = glmmTMB(update(base.formula,  ~ . + scale(battle_salience)), data = projects.trunc.bat, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "scale(battle_salience)", 0.16)
# 
# mod = glmmTMB(update(base.formula,  ~ . + scale(battle_prod)), data = projects.trunc.bat, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "scale(battle_prod)")
# 
# mod = glmmTMB(update(base.formula,  ~ . + scale(first_instantiation)), data = projects.trunc.bat, family = "truncated_nbinom2")
# compare(backers.mod.base, mod, "scale(first_instantiation)")
```
