---
title: "GoFundMe — Backers"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(glmmTMB)
library(gridExtra)
library(glue) # for pretty printing
library(tictoc) # for cell/function profiling
```

## GoFundMe Analysis of Backers

```{r}
projects = read_csv("../../data/processed/gofundme_projects_clean.csv")
projects = within(projects, {
  year = factor(year)
  month = factor(month)
  day_of_week = factor(day_of_week)
})
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

# Backers

```{r}
ggplot(projects) + labs(x="Number of Backers", title="Number of Backers Density") +
  geom_density(aes(backers))
```

Run a quick data dispersion test (see Rice 1995):

```{r}
pchisq(2 * sum(projects$backers * log(projects$backers / mean(projects$backers))), length(projects$backers) - 1, lower.tail = F)
```

H0: The data are fit well by a Poisson Distribution
H1: Poisson fails to fit the data well

The Poisson distribution obviously does not fit the data well since p approx 0. Let's use a NegBin instead, which can account for differences in the mean and variance.

```{r}
projects %>%
  ggplot(aes(goal, backers)) + labs(title="Goal Amount Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(duration_float, backers)) + labs(title="Duration Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(text_length_words, backers)) + labs(title="Text Length Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(photos, backers)) + labs(title="Photos Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects %>%
  ggplot(aes(updates, backers)) + labs(title="Updates Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(friends, backers)) + labs(title="FB Friends Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(shares, backers)) + labs(title="FB Shares Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects %>%
  ggplot(aes(cancer_type, backers)) + labs(title="Cancer Types") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

Establish the base formula to build models off of:

```{r}
base.formula = backers ~  shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,3)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(model.new)$coefficients$cond[key, ])
  cis = confint(model.new, parm=paste("cond.", key, sep = ""), method="wald")
  print(glue("beta: {round(effect[1],3)} (SE: {round(effect[2],3)}) (CI: {round(cis[1],3)}, {round(cis[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 3)}"))
  print(glue("rate ratio: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% (CI: {round((exp(cis[1]*multiplier) - 1)*100,1)}%, {round((exp(cis[2]*multiplier) - 1)*100,1)}%)"))
  print(glue(""))
}
```

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma

Key to interpretation is the log link used here

It might be the case that a quasi-Poisson model fits better, see:
https://digitalcommons.unl.edu/cgi/viewcontent.cgi?article=1141&context=usdeptcommercepub

Here, negative binomial has a lower residual deviance than quasi-poisson. Therefore we use NegBin.

Inherently, the number of backers must be > 0, thus we model using a truncated NegBin fit.

The coefficients of each model can be exponentiated to get the Incident Rate Ratio. 

## Any Metaphor

Null: The presence of metaphor does not significantly predict the total number of donors, compared to literal campaigns.

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects, family = "truncated_nbinom2")
summary(backers.mod)
```

### Results

```{r any metaphor}
mod = glmmTMB(update(f,  ~ . + any_metaphor), data = projects, family = "truncated_nbinom2")
compare(backers.mod, mod, "any_metaphorTRUE")

mod = glmmTMB(update(base.formula,  ~ . + any_metaphor), data = projects, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "any_metaphorTRUE")
```

## Both Metaphors

Null: The presence of both metaphor families (battle and journey) does not significantly predict the total number of donors, compared to literal campaigns.

```{r}
projects.both = projects[projects$no_metaphor | projects$both_metaphor, ] # only projects with both or none
```

N = `r nrow(projects.both)`

```{r}
projects.both %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(both_metaphor, backers, fill=both_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.both[projects.both$both_metaphor == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.both[projects.both$both_metaphor, ]$backers), lty=2, color="blue")

```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.both, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.both, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects.both, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.both, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r both metaphors}
mod = glmmTMB(update(f,  ~ . + both_metaphor), data = projects.both, family = "truncated_nbinom2")
compare(backers.mod, mod, "both_metaphorTRUE")

mod = glmmTMB(update(base.formula,  ~ . + both_metaphor), data = projects.both, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "both_metaphorTRUE")
```

## Compared Metaphor

Null1: Only using battle metaphors within the campaign text does not significantly predict the number of backers, compared to campaigns which only use journey metaphors

```{r}
projects.comp = projects[projects$any_metaphor & !projects$both_metaphor, ]
```
  
N = `r nrow(projects.comp)`

```{r}
cbind(projects.comp %>% filter(only_battle) %>% select(backers) %>% summary(),
      projects.comp %>% filter(only_journey) %>% select(backers) %>% summary())
```


```{r}
projects.comp %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, backers, fill=only_battle)) +
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.comp[projects.comp$only_battle, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.comp[projects.comp$only_battle, ]$backers), lty=2, color="blue")
```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.comp, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.comp, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.comp, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects.comp, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.comp, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r some metaphors reduced}
mod = glmmTMB(update(f,  ~ . + only_battle), data = projects.comp, family = "truncated_nbinom2")
compare(backers.mod, mod, "only_battleTRUE")
```

```{r some metaphors full}
mod = glmmTMB(update(base.formula,  ~ . + only_battle), data = projects.comp, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "only_battleTRUE")
```

## Only Journey

Null: Campaigns with only journey metaphors are not significantly more predictive of the total number of donors, compared to literal campaigns.

```{r}
projects.some.jor = projects[projects$only_journey | projects$no_metaphor, ]
```

```{r}
nrow(projects.some.jor)
table(projects.some.jor$only_journey)
```

```{r}
cbind(projects.some.jor %>% filter(!only_journey) %>% select(backers) %>% summary(),
      projects.some.jor %>% filter(only_journey) %>% select(backers) %>% summary())

projects.some.jor %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_journey, backers, fill=only_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some.jor[projects.some.jor$only_journey == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some.jor[projects.some.jor$only_journey, ]$backers), lty=2, color="blue")
```

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.some.jor, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.some.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmmTMB(f, data = projects.some.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.some.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects.some.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.some.jor, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r only journey}
mod = glmmTMB(update(f,  ~ . + only_journey), data = projects.some.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "only_journeyTRUE")

mod = glmmTMB(update(base.formula,  ~ . + only_journey), data = projects.some.jor, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "only_journeyTRUE")
```

## Journey Modulation

```{r}
projects.jor = projects[projects$journey_metaphor > 0, ]
```

N = `r nrow(projects.jor)`

```{r}
cbind(summary(projects.jor$journey_salience),
      summary(projects.jor$journey_rare),
      summary(projects.jor$journey_early))
```

```{r}
p1 = projects.jor %>%
  ggplot(aes(journey_salience, backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.jor %>%
  ggplot(aes(journey_rare, backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.jor %>%
  ggplot(aes(journey_early, backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.jor, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmmTMB(f, data = projects.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmmTMB(f, data = projects.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmmTMB(f, data = projects.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.jor, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.jor, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r journey modulation reduced}
mod = glmmTMB(update(f,  ~ . + journey_salience), data = projects.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "journey_salience")

mod = glmmTMB(update(f,  ~ . + journey_rare), data = projects.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "journey_rare")

mod = glmmTMB(update(f,  ~ . + journey_early), data = projects.jor, family = "truncated_nbinom2")
compare(backers.mod, mod, "journey_early")
```

```{r journey modulation full}
mod = glmmTMB(update(base.formula,  ~ . + journey_salience), data = projects.jor, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "journey_salience")

mod = glmmTMB(update(base.formula,  ~ . + journey_rare), data = projects.jor, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "journey_rare")

mod = glmmTMB(update(base.formula,  ~ . + journey_early), data = projects.jor, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "journey_early")
```

## Only Battle

Null: Campaigns with only battle metaphors are not significantly more predictive of the total number of donors, compared to literal campaigns.

```{r}
projects.some.bat = projects[projects$only_battle | projects$no_metaphor, ]
```

```{r}
nrow(projects.some.bat)
table(projects.some.bat$only_battle)
```

```{r}
cbind(projects.some.bat %>% filter(!only_battle) %>% select(backers) %>% summary(),
      projects.some.bat %>% filter(only_battle) %>% select(backers) %>% summary())

projects.some.bat %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, backers, fill=only_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.some.bat[projects.some.bat$only_battle == F, ]$backers), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.some.bat[projects.some.bat$only_battle, ]$backers), lty=2, color="blue")
```

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.some.bat, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.some.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.some.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmmTMB(f, data = projects.some.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.some.bat, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r only battle}
mod = glmmTMB(update(f,  ~ . + only_battle), data = projects.some.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "only_battleTRUE")

mod = glmmTMB(update(base.formula,  ~ . + only_battle), data = projects.some.bat, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "only_battleTRUE")
```

## Battle Modulation

```{r}
projects.bat = projects[projects$battle_metaphor > 0, ]
```

N = `r nrow(projects.bat)`

```{r}
cbind(summary(projects.bat$battle_salience),
      summary(projects.bat$battle_rare),
      summary(projects.bat$battle_early))
```

```{r}
p1 = projects.bat %>%
  ggplot(aes(battle_salience, backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.bat %>%
  ggplot(aes(battle_rare, backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.bat %>%
  ggplot(aes(battle_early, backers)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
backers.mod.base = glmmTMB(base.formula, data = projects.bat, family = "truncated_nbinom2")
# drop1(backers.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmmTMB(f, data = projects.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmmTMB(f, data = projects.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmmTMB(f, data = projects.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmmTMB(f, data = projects.bat, family = "truncated_nbinom2"), test="Chisq")
```

```{r}
backers.mod = glmmTMB(f, data = projects.bat, family = "truncated_nbinom2")
# summary(backers.mod)
```

### Results

```{r battle modulation reduced}
mod = glmmTMB(update(f,  ~ . + battle_salience), data = projects.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "battle_salience")

mod = glmmTMB(update(f,  ~ . + battle_rare), data = projects.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "battle_rare")

mod = glmmTMB(update(f,  ~ . + battle_early), data = projects.bat, family = "truncated_nbinom2")
compare(backers.mod, mod, "battle_early")
```

```{r battle modulation full}
mod = glmmTMB(update(base.formula,  ~ . + battle_salience), data = projects.bat, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "battle_salience")

mod = glmmTMB(update(base.formula,  ~ . + battle_rare), data = projects.bat, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "battle_rare")

mod = glmmTMB(update(base.formula,  ~ . + battle_early), data = projects.bat, family = "truncated_nbinom2")
compare(backers.mod.base, mod, "battle_early")
```
