---
title: "GoFundMe — Mean Donation"
output: 
  html_document:
    toc: true
    toc_float: true
---

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma
http://rstudio-pubs-static.s3.amazonaws.com/5691_192685385fc445c9b3fb1619960a20e2.html


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(gridExtra)
library(glue) # for pretty printing
library(tictoc) # for cell/function profiling
```

## GoFundMe Analysis of Mean Donation

```{r}
projects = read_csv("../../data/processed/gofundme_projects_clean.csv")
projects$month = factor(projects$month)
projects$day_of_week = factor(projects$day_of_week)
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

# Mean Donation

```{r}
upper_limit = quantile(projects$mean_donation, 0.995) # remove the top 0.5% of projects, eventually create models with these data included
nrow(projects[projects$mean_donation > upper_limit, ])
projects.trunc = projects[projects$mean_donation < upper_limit, ]

projects.trunc %>%
  ggplot() + labs(title="Mean Donation Density") +
  geom_density(aes(mean_donation))

projects.trunc %>%
  ggplot() + geom_qq(aes(sample=mean_donation), distribution = qexp) + geom_qq_line(aes(sample=mean_donation), distribution = qexp)
```

```{r}
projects.trunc %>%
  ggplot(aes(goal, mean_donation)) + labs(title="Goal Amount Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(duration_float, mean_donation)) + labs(title="Duration Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(text_length_words, mean_donation)) + labs(title="Text Length Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(photos, mean_donation)) + labs(title="Photos Distribution") +
  geom_point(alpha=0.1) +
  theme_minimal()

projects.trunc %>%
  ggplot(aes(updates, mean_donation)) + labs(title="Updates Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects.trunc %>%
  ggplot(aes(friends, mean_donation)) + labs(title="FB Friends Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects.trunc %>%
  ggplot(aes(shares, mean_donation)) + labs(title="FB Shares Distribution") +
  geom_point(alpha=0.1) + 
  theme_minimal()

projects.trunc %>%
  ggplot(aes(cancer_type, mean_donation)) + labs(title="Cancer Types") +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

 - https://stats.stackexchange.com/questions/142013/correct-glmer-distribution-family-and-link-for-a-continuous-zero-inflated-data-s
 
The data look like a Gamma, so we model with Gamma and a log link (see above answer for reason). It might be nice 

Ideally, I could run a distributional test and confirm (or reject) this intuition.

Establish the base formula to build models off of:

```{r}
base.formula = mean_donation ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t New AIC: {round(a$AIC[2], 1)}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,4)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(mod)$coefficients[key, ])
  print(glue("beta: {round(effect[1],4)} (+/- {round(effect[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 4)}"))
  print(glue("rate ratio: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% ({round((exp((effect[1] - effect[2])*multiplier) - 1)*100, 1)}% to {round((exp((effect[1] + effect[2])*multiplier) - 1)*100, 1)}%)"))
  print(glue(""))
}
```

https://stats.stackexchange.com/questions/96972/how-to-interpret-parameters-in-glm-with-family-gamma

Key to interpretation is the log link used here

To put the results from the continuous predictors on interpretable scales, we use a multiplier within the exponent (see `factor` in `compare()`). For example, if the multiplier is 1, this leads to: for a one unit increase in this predictor, we see an *x*-fold increase in the DV.

```{r}
p = function(var, scl=1, digits=6, mult=1.00, mask=T) {
  mu = mean(projects[mask, var])
  sd = sd(projects[mask, var])
  print(glue("Var: {var}\t Mean: {round(mu,digits)*scl}\t SD: {round(sd,digits)*scl}\t Scale (x{round(mult, 2)}): {paste(round(mult*sd + mu, digits)*scl)}"))
}
# p("journey_salience", scl = 1000, digits = 5, mult = 0.6)
# p("battle_salience", scl = 1000, digits = 5, mult = 0.16)
# p("journey_prod", digits = 4, mask = projects$journey_metaphor > 0)
# p("battle_prod", digits = 4, mask = projects$battle_metaphor > 0)
# p("first_instantiation", digits = 4, mask = projects$journey_metaphor > 0, mult = 1.6)
# p("first_instantiation", digits = 4, mask = projects$battle_metaphor > 0, mult = 1.6)
```

## Any Metaphor

Examine: does having any instance of metaphor influence mean donation?

Null: having any metaphor is not significantly different from having no metaphor

```{r}
projects.trunc %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(any_metaphor, mean_donation, fill=any_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc[projects.trunc$any_metaphor == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc[projects.trunc$any_metaphor, ]$mean_donation), lty=2, color="blue")
```

```{r}
mean.mod.base = glmer(base.formula, data = projects.trunc, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.trunc, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.trunc, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.trunc, family = Gamma(link = "log")), test="Chisq")
```

```{r}
# f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.trunc, family = Gamma(link = "log")), test="Chisq")
```



```{r}
mean.mod = glmer(f, data = projects.trunc, family = Gamma(link = "log"))
summary(mean.mod)
```

### Results

```{r any metaphor}
mod = glmer(update(f,  ~ . + any_metaphor), data = projects.trunc, family = Gamma(link = "log"))
compare(mean.mod, mod, "any_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + any_metaphor), data = projects.trunc, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "any_metaphorTRUE")
```

## Both Metaphors

Examine: does having both metaphor families present influence mean donation?

Null: having both metaphor families is not significantly different from having no metaphor

```{r}
projects.trunc.both = projects.trunc[(1-projects.trunc$any_metaphor) | projects.trunc$both_metaphor, ] # only projects with both or none
```

N = `r nrow(projects.trunc.both)`

```{r}
projects.trunc.both %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(both_metaphor, mean_donation, fill=both_metaphor)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.both[projects.trunc.both$both_metaphor == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.both[projects.trunc.both$both_metaphor, ]$mean_donation), lty=2, color="blue")
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.trunc.both, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - month)
# drop1(glmer(f, data = projects.trunc.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.trunc.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.trunc.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.trunc.both, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.trunc.both, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r both metaphors}
mod = glmer(update(f,  ~ . + both_metaphor), data = projects.trunc.both, family = Gamma(link = "log"))
compare(mean.mod, mod, "both_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + both_metaphor), data = projects.trunc.both, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "both_metaphorTRUE")
```

## Some Metaphor

Examine: does having only journey/battle, or dominant journey/battle, influence mean donation?

Null: having only journey/battle, or dominant journey/battle, is not significantly different from negative

If journey is not the dominant metaphor, that means battle is or there are equal amounts of each family
If journey is not the only metaphor family, that means there is at least some battle metaphor

Dominant Journey:
Null: There is no difference in outcomes when journey dominates compared to when battle dominates or there is no dominant family.

Dominant Battle:
Null: There is no difference in outcomes when battle dominates compared to when journey dominates or there is no dominant family.

Only journey:
Null: There is no difference in outcomes when journey is the only metaphor family present compared to when there is also battle metaphor.

```{r}
projects.trunc.some = projects.trunc[projects.trunc$any_metaphor, ]
```
  
N = `r nrow(projects.trunc.some)`

```{r}
p1 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(dom_journey, mean_donation, fill=dom_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_journey == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_journey, ]$mean_donation), lty=2, color="blue")

p2 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(dom_battle, mean_donation, fill=dom_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_battle == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$dom_battle, ]$mean_donation), lty=2, color="blue")

p3 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_journey, mean_donation, fill=only_journey)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_journey == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_journey, ]$mean_donation), lty=2, color="blue")

p4 = projects.trunc.some %>%
  ggplot() + theme_minimal() +
  geom_violin(aes(only_battle, mean_donation, fill=only_battle)) + 
  scale_fill_manual(values = c("FALSE" = alpha("red", 0.5), "TRUE" = alpha("blue", 0.5)), guide=F) + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_battle == F, ]$mean_donation), lty=2, color="red") + 
  geom_hline(yintercept = mean(projects.trunc.some[projects.trunc.some$only_battle, ]$mean_donation), lty=2, color="blue")

grid.arrange(p1, p2, p3, p4, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.trunc.some, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.trunc.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.trunc.some, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.trunc.some, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r some metaphors reduced}
mod = glmer(update(f,  ~ . + dom_journey), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "dom_journeyTRUE")

mod = glmer(update(f,  ~ . + dom_battle), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "dom_battleTRUE")

mod = glmer(update(f,  ~ . + only_journey), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_journeyTRUE")

mod = glmer(update(f,  ~ . + only_battle), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod, mod, "only_battleTRUE")
```

```{r some metaphors full}
mod = glmer(update(base.formula,  ~ . + dom_journey), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "dom_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + dom_battle), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "dom_battleTRUE")

mod = glmer(update(base.formula,  ~ . + only_journey), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.trunc.some, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "only_battleTRUE")
```

## Journey

```{r}
projects.trunc.jor = projects.trunc[projects.trunc$journey_metaphor > 0, ]
```

N = `r nrow(projects.trunc.jor)`

```{r}
p1 = projects.trunc.jor %>%
  ggplot(aes(scale(journey_salience), mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.trunc.jor %>%
  ggplot(aes(scale(journey_prod), mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.trunc.jor %>%
  ggplot(aes(scale(first_instantiation), mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.trunc.jor, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - updates_sc)
# drop1(glmer(f, data = projects.trunc.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.trunc.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.trunc.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.trunc.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.trunc.jor, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.trunc.jor, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r journey specific reduced}
mod = glmer(update(f,  ~ . + scale(journey_salience)), data = projects.trunc.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "scale(journey_salience)", 0.6)

mod = glmer(update(f,  ~ . + scale(journey_prod)), data = projects.trunc.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "scale(journey_prod)")

mod = glmer(update(f,  ~ . + scale(first_instantiation)), data = projects.trunc.jor, family = Gamma(link = "log"))
compare(mean.mod, mod, "scale(first_instantiation)")
```

```{r journey specific full}
mod = glmer(update(base.formula,  ~ . + scale(journey_salience)), data = projects.trunc.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "scale(journey_salience)", 0.6)

mod = glmer(update(base.formula,  ~ . + scale(journey_prod)), data = projects.trunc.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "scale(journey_prod)")

mod = glmer(update(base.formula,  ~ . + scale(first_instantiation)), data = projects.trunc.jor, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "scale(first_instantiation)")
```

## Battle

```{r}
projects.trunc.bat = projects.trunc[projects.trunc$battle_metaphor > 0, ]
```

N = `r nrow(projects.trunc.bat)`

```{r}
p1 = projects.trunc.bat %>%
  ggplot(aes(scale(battle_salience), mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p2 = projects.trunc.bat %>%
  ggplot(aes(scale(battle_prod), mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

p3 = projects.trunc.bat %>%
  ggplot(aes(scale(first_instantiation), mean_donation)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm", se = F, color="red") + geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = F, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
mean.mod.base = glmer(base.formula, data = projects.trunc.bat, family = Gamma(link = "log"))
# drop1(mean.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.trunc.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.trunc.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.trunc.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.trunc.bat, family = Gamma(link = "log")), test="Chisq")
```

```{r}
mean.mod = glmer(f, data = projects.trunc.bat, family = Gamma(link = "log"))
# summary(mean.mod)
```

### Results

```{r battle specific reduced}
mod = glmer(update(f,  ~ . + scale(battle_salience)), data = projects.trunc.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "scale(battle_salience)", 0.16)

mod = glmer(update(f,  ~ . + scale(battle_prod)), data = projects.trunc.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "scale(battle_prod)")

mod = glmer(update(f,  ~ . + scale(first_instantiation)), data = projects.trunc.bat, family = Gamma(link = "log"))
compare(mean.mod, mod, "scale(first_instantiation)")
```

```{r battle specific full}
mod = glmer(update(base.formula,  ~ . + scale(battle_salience)), data = projects.trunc.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "scale(battle_salience)", 0.16)

mod = glmer(update(base.formula,  ~ . + scale(battle_prod)), data = projects.trunc.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "scale(battle_prod)")

mod = glmer(update(base.formula,  ~ . + scale(first_instantiation)), data = projects.trunc.bat, family = Gamma(link = "log"))
compare(mean.mod.base, mod, "scale(first_instantiation)")
```
