---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
theme = theme_minimal()
```

# Experimental Analysis

## Load and Clean Data

Created via `clean_data.R`.

```{r}
data = read_csv("clean_pilot.csv", col_types = cols())

data$cond_sex = factor(data$cond_sex, levels = c("male", "female"))
data$cond_metaphor = factor(data$cond_metaphor, levels = c("literal", "battle", "journey"))

data$cond = paste(data$cond_sex, "_", data$cond_metaphor, sep="")

data$urgent = as.integer(data$urgent)
data$serious = as.integer(data$serious)
data$sympathy = as.integer(data$sympathy)
data$peace = as.integer(data$peace)
data$guilty = as.integer(data$guilty)


nrow(data)
head(data)
```

```{r}
ggplot(data) + geom_density(aes(rt_trial / (1000 * 60))) + labs(title = "Main Trial RT", x = "Response Time (mins)")
```

```{r}
summary(data$donation)
mean(data$donation == 1)
mean(data$donation == 50)
```

## Comparison of Conditions

```{r}
ggplot(data) + theme + 
  geom_density(aes(donation, color = cond)) +
  labs(x = "Donation Amount", y = "Density", title = "Donation Distributions by Condition", fill = "Condition") +
  lims(x=c(0, 50))
```

```{r}
data %>%
  group_by(cond_sex, cond_metaphor) %>%
  summarise(avg = mean(donation)) %>%
  ggplot() + theme +
  geom_point(aes(cond_metaphor, avg, color = cond_sex, shape = cond_sex), size=4) +
  geom_line(aes(cond_metaphor, avg, group = cond_sex), lty=2) +
  labs(x = "Condition: Metaphor", y = "Mean Donation", title = "Condition Interactions") #, color = "Condition:\nSex"
```

```{r}
data %>%
  group_by(cond_sex, cond_metaphor) %>%
  summarise(avg = mean(donation), sd = sd(donation)) %>%
  ggplot() + theme +
  geom_bar(aes(cond_metaphor, avg, fill = cond_sex), stat="identity", position = "dodge") +
  geom_errorbar(aes(cond_metaphor, ymin = avg - 2*sd, ymax = avg + 2*sd), position = "dodge", width = 0.2) +
  labs(x = "Condition: Metaphor", y = "Mean Donation")
```


## Covariates

```{r}
ggplot(data) + theme +
  geom_density(aes(total_time / (1000 * 60))) +
  labs(x = "Total Duration (mins)", y = "Density", title = "Total Duration Distribution")

ggplot(data) + theme +
  geom_bar(aes(urgent, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Urgent", y = "Proportion", title = "Urgent Distribution", subtitle = "\"Her situation is urgent.\"")

ggplot(data) + theme +
  geom_bar(aes(serious, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Serious", y = "Proportion", title = "Serious Distribution", subtitle = "\"Her situation is serious.\"")

ggplot(data) + theme +
  geom_bar(aes(sympathy, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Sympathy", y = "Proportion", title = "Sympathy Distribution", subtitle = "\"Her situation is one I sympathize with.\"")
```

```{r}
sympathy.model = lm(sympathy ~ cond_metaphor, data = data)

summary(sympathy.model)
anova(sympathy.model)
```

```{r}
urgent.model = lm(urgent ~ cond_metaphor, data = data)

summary(urgent.model)
anova(urgent.model)
```

```{r}
serious.model = lm(serious ~ cond_metaphor, data = data)

summary(serious.model)
anova(serious.model)
```

```{r}
data$investment = data$serious + data$urgent + data$sympathy
```

```{r}
data
```


```{r}
investment.model = lm(investment ~ cond_metaphor*cond_sex + english, data = data)

summary(investment.model)
anova(investment.model)
```

```{r}
hist(resid(investment.model))
```




```{r}
ggplot(data) + theme +
  geom_bar(aes(peace, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Peace", y = "Proportion", title = "Peace Distribution", subtitle = "\"She can make peace with her experience.\"")

ggplot(data) + theme +
  geom_bar(aes(guilty, group=1, y=..prop..)) +
  scale_x_discrete(limits = seq(0,6)) +
  labs(x = "Guilty", y = "Proportion", title = "Guilty Distribution", subtitle = "\"She will feel guilty that she hasn’t done enough if she does not recover.\"")
```

```{r}
s = data %>% 
  group_by(cond_metaphor) %>% 
  summarize(med = median(guilty), 
            Q1 = quantile(guilty, 0.25),
            Q3 = quantile(guilty, 0.75))

ggplot(s) + theme +
  geom_point(aes(cond_metaphor, med), shape=4, size=3) +
  geom_errorbar(aes(x=cond_metaphor, ymin=Q1, ymax=Q3,
                    width=0.1)) +
  lims(y=c(0,6)) +
  labs(x = "Metaphor Condition", y = "Score", title = "Guilty Scores")
```

```{r}
s = data %>% 
  group_by(cond_metaphor) %>% 
  summarize(med = median(peace), 
            Q1 = quantile(peace, 0.25),
            Q3 = quantile(peace, 0.75))

ggplot(s) + theme +
  geom_point(aes(cond_metaphor, med), shape=4, size=3) +
  geom_errorbar(aes(x=cond_metaphor, ymin=Q1, ymax=Q3,
                    width=0.1)) +
  lims(y=c(0,6)) +
  labs(x = "Metaphor Condition", y = "Score", title = "Peace Scores")
```

```{r}
guilt.model = lm(guilty ~ cond_metaphor*cond_sex, data = data)

summary(guilt.model)
anova(guilt.model)
```

```{r}
peace.model = lm(peace ~ cond_metaphor*cond_sex, data = data)

summary(peace.model)
anova(peace.model)
```

## Demographics

```{r}
ggplot(data) +
  geom_density(aes(donation, color=self_cancer)) +
  lims(x = c(0, 50)) +
  labs(x = "Donation Amount", y = "Density", color = "Self Cancer", title = "Donation Distributions by Education Level")

ggplot(data) +
  geom_density(aes(donation, color=ff_cancer)) +
  lims(x = c(0, 50)) +
  labs(x = "Donation Amount", y = "Density", color = "Friends and Family\nCancer", title = "Donation Distributions by Friends and Family Cancer")

ggplot(data) +
  geom_density(aes(donation, color=gender)) +
  lims(x = c(0, 50)) +
  labs(x = "Donation Amount", y = "Density", color = "Gender", title = "Donation Distributions by Gender")

ggplot(data) +
  geom_density(aes(donation, color=education)) +
  lims(x = c(0, 50)) +
  labs(x = "Donation Amount", y = "Density", color = "Education Level", title = "Donation Distributions by Education Level")

ggplot(data) +
  geom_density(aes(donation, color=socioeconomic)) +
  lims(x = c(0, 50)) +
  labs(x = "Donation Amount", y = "Density", color = "Socioeconomic Level", title = "Donation Distributions by Socioeconomic Level")

ggplot(data) +
  geom_density(aes(donation, color=english)) +
  lims(x = c(0, 50)) +
  labs(x = "Donation Amount", y = "Density", color = "Native English", title = "Donation Distributions by Native English")
```

## Regression

**Does simply having either metaphor family present explain donation behavior?**

Note: with more data, will include covariates

```{r}
data$cond_any = (data$cond_metaphor != "literal")
full.model = lm(donation ~ cond_any*cond_sex, data = data) # + gender + education + socioeconomic + english

summary(full.model)
```

**Does either the battle or the journey metaphor family explain donation behavior beyond the literal condition?**

```{r}
full.model = lm(donation ~ cond_metaphor*cond_sex + gender + education + socioeconomic + english, data = data)

summary(full.model)
```





