---
title: "GoFundMe — Status"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(gridExtra)
library(glue) # for pretty printing
```

## GoFundMe Analysis of Status

```{r}
projects = read_csv("../../data/processed/gofundme_projects_clean.csv")
projects = within(projects, {
  year = factor(year)
  month = factor(month)
  day_of_week = factor(day_of_week)
  status = factor(status)
})
```

In total, we have N=`r nrow(projects)` IID samples to work with.

Removed all random variabes except year because they didn't help explain any variance in the data beyond what the residuals could capture. Year is a reasonable random effect as well (see Variance Components, Searle et al 2006)

Nesting and Chi2 differences:
https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf

# Status

```{r}
th = theme_minimal()
projects %>%
  ggplot() + th + labs(title="Goal Amount Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(goal, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Duration Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(duration_float, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Text Length Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(text_length_words, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Photos Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(photos, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Updates Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(updates, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="FB Friends Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(friends, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Comments Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(comments, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="FB Shares Distribution") + guides(color=guide_legend(title="Status")) +
  geom_density(aes(shares, color=fct_recode(factor(status), "Successful"="1", "Failed"="0")))

projects %>%
  ggplot() + th + labs(title="Cancer Type Counts") + guides(fill=guide_legend(title="Status")) +
  geom_bar(aes(x=cancer_type, fill=fct_recode(factor(status), "Successful"="1", "Failed"="0")), position="dodge") +
  theme(axis.text.x=element_text(angle = 60, hjust=1))
```

Establish the base formula to build models off of:

```{r}
base.formula = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)
```

Create a helper function to easily compare two models and pretty print the output:

```{r}
compare = function(model.old, model.new, key, multiplier=1.0) {
  a = anova(model.old, model.new)
  p = a$`Pr(>Chisq)`[2]
  print(glue("Variable: {key}"))
  print(glue("DF diff: {a$`Chi Df`[2]}\t\t Chisq: {round(a$Chisq[2],1)}\t P(>chisq) = {round(p,3)} {if (p < 0.05) '(significant)' else ''})"))
  effect = as.numeric(summary(model.new)$coefficients[key, ])
  cis = confint(model.new, parm=key, method="Wald")
  print(glue("beta: {round(effect[1],3)} (SE: {round(effect[2],3)}) (CI: {round(cis[1],3)}, {round(cis[2],3)})\t stat: {round(effect[3], 2)} => P(>|z|) = {round(effect[4], 3)}"))
  print(glue("odds change: {round((exp(effect[1]*multiplier) - 1)*100, 1)}% (CI: {round((exp(cis[1]*multiplier) - 1)*100,1)}%, {round((exp(cis[2]*multiplier) - 1)*100,1)}%)"))
  print(glue(""))
}
```

## Any Metaphor

Null: The presence of metaphor does not significantly predict the success, compared to literal campaigns.

```{r}
projects %>%
  ggplot() + th + geom_bar(aes(status, fill=any_metaphor), position="dodge")
```

```{r}
status.mod.base = glmer(base.formula, data = projects, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects, family = "binomial")
# summary(status.mod)
```

### Results

```{r any metaphor}
mod = glmer(update(f,  ~ . + any_metaphor), data = projects, family = "binomial")
compare(status.mod, mod, "any_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + any_metaphor), data = projects, family = "binomial")
compare(status.mod.base, mod, "any_metaphorTRUE")
```

## Both Metaphors

Null: The presence of both metaphor families (battle and journey) does not significantly predict the success, compared to literal campaigns.

```{r}
projects.both = projects[projects$no_metaphor | projects$both_metaphor, ] # only projects with both or none
```

N = `r nrow(projects.both)`

```{r}
projects %>%
  ggplot() + th + geom_bar(aes(status, fill=both_metaphor), position="dodge")
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.both, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.both, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.both, family = "binomial")
# summary(status.mod)
```

### Results

```{r both metaphors}
mod = glmer(update(f,  ~ . + both_metaphor), data = projects.both, family = "binomial")
compare(status.mod, mod, "both_metaphorTRUE")

mod = glmer(update(base.formula,  ~ . + both_metaphor), data = projects.both, family = "binomial")
compare(status.mod.base, mod, "both_metaphorTRUE")
```

## Compared Metaphor

Null1: Only using battle metaphors within the campaign text does not significantly predict the success, compared to campaigns which only use journey metaphors

```{r}
projects.comp = projects[projects$any_metaphor & !projects$both_metaphor, ]
```
  
N = `r nrow(projects.comp)`

```{r}
table(projects.comp$only_battle, projects.comp$status)
```

```{r}
projects.comp  %>%
  ggplot() + th +
  geom_bar(aes(status, fill=only_battle), position = "dodge") + 
  lims(y=c(0,2000)) +
  labs(title="Battle Campaigns and Success", fill = "Battle Campaigns")
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.comp, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.comp, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.comp, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.comp, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.comp, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.comp, family = "binomial")
# summary(status.mod)
```

### Results

```{r some metaphors reduced}
mod = glmer(update(f,  ~ . + only_battle), data = projects.comp, family = "binomial")
compare(status.mod, mod, "only_battleTRUE")
```

```{r some metaphors full}
mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.comp, family = "binomial")
compare(status.mod.base, mod, "only_battleTRUE")
```

## Only Journey

Null: Campaigns with only journey metaphors are not significantly more predictive of the success, compared to literal campaigns.

```{r}
projects.some.jor = projects[projects$only_journey | projects$no_metaphor, ]
```

```{r}
nrow(projects.some.jor)
table(projects.some.jor$only_journey)
```

```{r}
cbind(projects.some.jor %>% filter(!only_journey) %>% select(status) %>% summary(),
      projects.some.jor %>% filter(only_journey) %>% select(status) %>% summary())

projects.some.jor %>%
  ggplot() + th +
  geom_bar(aes(status, fill=only_journey), position = "dodge") +
  labs(title="Only Journey")
```

```{r}
status.mod.base = glmer(base.formula, data = projects.some.jor, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.some.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.some.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.some.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.some.jor, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.some.jor, family = "binomial")
# summary(status.mod)
```

### Results

```{r only journey}
mod = glmer(update(f,  ~ . + only_journey), data = projects.some.jor, family = "binomial")
compare(status.mod, mod, "only_journeyTRUE")

mod = glmer(update(base.formula,  ~ . + only_journey), data = projects.some.jor, family = "binomial")
compare(status.mod.base, mod, "only_journeyTRUE")
```

## Journey Modulation

```{r}
projects.jor = projects[projects$journey_metaphor > 0, ]
```

N = `r nrow(projects.jor)`

```{r}
cbind(summary(projects.jor$journey_salience),
      summary(projects.jor$journey_rare),
      summary(projects.jor$journey_early))
```

```{r}
p1 = projects.jor %>%
  ggplot() + th +
  geom_violin(aes(status, journey_salience, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$journey_salience), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$journey_salience), lty=2, color="blue")

p2 = projects.jor %>%
  ggplot() + th +
  geom_violin(aes(status, journey_rare, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$journey_rare), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$journey_rare), lty=2, color="blue")

p3 = projects.jor %>%
  ggplot() + th +
  geom_violin(aes(status, journey_early, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 0, ]$journey_early), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.jor[projects.jor$status == 1, ]$journey_early), lty=2, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.jor, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - cancer_type)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.jor, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.jor, family = "binomial")
# summary(status.mod)
```

### Results

```{r journey modulation reduced}
mod = glmer(update(f,  ~ . + journey_salience), data = projects.jor, family = "binomial")
compare(status.mod, mod, "journey_salience")

mod = glmer(update(f,  ~ . + journey_rare), data = projects.jor, family = "binomial")
compare(status.mod, mod, "journey_rare")

mod = glmer(update(f,  ~ . + journey_early), data = projects.jor, family = "binomial")
compare(status.mod, mod, "journey_early")
```

```{r journey modulation full}
mod = glmer(update(base.formula,  ~ . + journey_salience), data = projects.jor, family = "binomial")
compare(status.mod.base, mod, "journey_salience")

mod = glmer(update(base.formula,  ~ . + journey_rare), data = projects.jor, family = "binomial")
compare(status.mod.base, mod, "journey_rare")

mod = glmer(update(base.formula,  ~ . + journey_early), data = projects.jor, family = "binomial")
compare(status.mod.base, mod, "journey_early")
```

## Only Battle

Null: Campaigns with only battle metaphors are not significantly more predictive of the success, compared to literal campaigns.

```{r}
projects.some.bat = projects[projects$only_battle | projects$no_metaphor, ]
```

```{r}
nrow(projects.some.bat)
table(projects.some.bat$only_battle)
```

```{r}
cbind(projects.some.bat %>% filter(!only_battle) %>% select(status) %>% summary(),
      projects.some.bat %>% filter(only_battle) %>% select(status) %>% summary())

projects.some.bat %>%
  ggplot() + th +
  geom_bar(aes(status, fill=only_battle), position = "dodge") +
  labs(title="Only Journey")
```

```{r}
base.formula = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + (1|year)

status.mod.base = glmer(base.formula, data = projects.some.bat, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.some.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.some.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.some.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.some.bat, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.some.bat, family = "binomial")
# summary(status.mod)
```

### Results

```{r only battle}
mod = glmer(update(f,  ~ . + only_battle), data = projects.some.bat, family = "binomial")
compare(status.mod, mod, "only_battleTRUE")

mod = glmer(update(base.formula,  ~ . + only_battle), data = projects.some.bat, family = "binomial")
compare(status.mod.base, mod, "only_battleTRUE")
```

## Battle Modulation

```{r}
projects.bat = projects[projects$battle_metaphor > 0, ]
```

N = `r nrow(projects.bat)`

```{r}
cbind(summary(projects.bat$battle_salience),
      summary(projects.bat$battle_rare),
      summary(projects.bat$battle_early))
```

```{r}
p1 = projects.bat %>%
  ggplot() + th +
  geom_violin(aes(status, battle_salience, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.bat[projects.bat$status == 0, ]$battle_salience), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.bat[projects.bat$status == 1, ]$battle_salience), lty=2, color="blue")

p2 = projects.bat %>%
  ggplot() + th +
  geom_violin(aes(status, battle_rare, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.bat[projects.bat$status == 0, ]$battle_rare), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.bat[projects.bat$status == 1, ]$battle_rare), lty=2, color="blue")

p3 = projects.bat %>%
  ggplot() + th +
  geom_violin(aes(status, battle_early, fill=status)) +
  scale_fill_manual(values = c("0" = alpha("red", 0.5), "1" = alpha("blue", 0.5)), guide=F) +
  geom_hline(yintercept = mean(projects.bat[projects.bat$status == 0, ]$battle_early), lty=2, color="red") +
  geom_hline(yintercept = mean(projects.bat[projects.bat$status == 1, ]$battle_early), lty=2, color="blue")

grid.arrange(p1, p2, p3, nrow=1)
```

Perform model selection to prevent overfitting:

```{r}
status.mod.base = glmer(base.formula, data = projects.bat, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - text_length_words_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - day_of_week)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - photos_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glmer(f, data = projects.bat, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glmer(f, data = projects.bat, family = "binomial")
# summary(status.mod)
```

### Results

```{r battle modulation reduced}
mod = glmer(update(f,  ~ . + battle_salience), data = projects.bat, family = "binomial")
compare(status.mod, mod, "battle_salience")

mod = glmer(update(f,  ~ . + battle_rare), data = projects.bat, family = "binomial")
compare(status.mod, mod, "battle_rare")

mod = glmer(update(f,  ~ . + battle_early), data = projects.bat, family = "binomial")
compare(status.mod, mod, "battle_early")
```

```{r battle modulation full}
mod = glmer(update(base.formula,  ~ . + battle_salience), data = projects.bat, family = "binomial")
compare(status.mod.base, mod, "battle_salience")

mod = glmer(update(base.formula,  ~ . + battle_rare), data = projects.bat, family = "binomial")
compare(status.mod.base, mod, "battle_rare")

mod = glmer(update(base.formula,  ~ . + battle_early), data = projects.bat, family = "binomial")
compare(status.mod.base, mod, "battle_early")
```

## Simple model

```{r}
base.formula = status ~ shares_sc + friends_sc + updates_sc + photos_sc + goal_sc + text_length_words_sc + duration_float_sc + cancer_type + month + day_of_week + year
```

```{r}
status.mod.base = glm(base.formula, data = projects, family = "binomial")
# drop1(status.mod.base, test="Chisq")
```

```{r}
f = update(base.formula,  ~ . - day_of_week)
# drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - duration_float_sc)
# drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - month)
# drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - text_length_words_sc)
# drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
f = update(f,  ~ . - friends_sc)
# drop1(glm(f, data = projects, family = "binomial"), test="Chisq")
```

```{r}
status.mod = glm(f, data = projects, family = "binomial")
# summary(status.mod)
```

```{r}
mod = glm(update(f, ~ . + any_metaphor), data = projects, family = "binomial")
summary(mod)
```

